---
title: "Stats_Physiology"
author: "Anna A. Hippmann"
date: "May 22nd, 2015"
output: 
  html_document: 
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Libraries used
``` {r libraries, eval=TRUE}
suppressPackageStartupMessages(library(lsmeans))
suppressPackageStartupMessages(library(phia))
suppressPackageStartupMessages(library(visreg))
suppressPackageStartupMessages(library(dplyr))
library(ggplot2)
library(knitr)
```

### Overview

<a id="BackUP"></a>

* __Background__: What I did with [Rick White](#RickWhite)
  + `z_all <- lm()` with all main effects and interaction - [z_all](#z_all)
  + `z <- lm()` without Species:Cu.level interaction - [z](#z)
  + `anova(z)` anova indicating where to look for significant effects and interacitons - [`anova(z)`](#anova_z)
  + `lsmeans()` to check for pairwise comparisons
    +lsmeans has changed quite a bit in newer version -> I am thinking about different post-hoc test
    
* __Background__: Using `phia` ("post hoc interaction association") package to check for [interaction](#phia_interaction)
* __Background__: Using `phia` to do [pairwise comparison](#phia_pariwise)


* Overview of [My Method](#MyMethod) to Analyze my Physiological Data
  + [Growthrate (dd-1)](#Growthrate.dd)
  + [Growthrate (d)](#Growthrate.spec)
  + [Growthrate (percent of umax)](#Growthrate.percent)
  + [Fv/Fm](#FvFm)
  + [Sigma](#Sigma)
  + [PQ Size](#PQ)
  + [Chl a per Cell Vol (fg/fL)](#Chla)
  + [Chl a per Cell (pg/cell)](#Chla.cell)
  + [Cell Size (um)](#cellsize)
  + [FeDFB uptake per cell (zmol/cell*h)](#FeDFB.cell)
  + [FeDFB uptake per cell surface area (zmol/um^2*h))](#FeDFB.cellvol)
  + [14C uptake - alpha (per cell)](#14C.alpha.cell)
  + [14C uptake - alpha (per Chl a)](#14C.alpha.chla)
  + [14C uptake - ek (per Chl a)](#14C.ek.chla)
  + [AOX - Alternative Oxidase (percent)](#AOX)
  + [Gross Production per Chl a (mol O2 / mol Chla * h)](#O2.Chla)
  + [Gross Production per cell (mol O2 / cell * h)](#O2.Cell)
  + [Gross Production per cell vol (mol O2 / cell vol * h)](#O2.Cell.vol)
  


#### BACKGROUND: 

<a id="RickWhite"><a>

## Run Down of what we did in SCARL meeting in May 2015


I met with Rick White from the "Statistical Consulting and Research Laboratory" [SCARL](http://www.stat.ubc.ca/SCARL/) at UBC to discuss my approach to analyze my physiological data statistically. The main question was, whether I would need to use a mixed effects model or a fixed effects model. Then how to actually go about analyzing it practically (i.e.which program/ package to use etc)

As per my experimental set up, I have **3 fixed effects**:

1) Species _(as I choose these 2 strains on purpose to test for differences between them)_

2) Fe-level

3) Cu-level

For this I will need to use 

1) the **function `lm()` = linear model**. 
2) then use `anova()` on the `lm object`
3) then use `lsmeans()` on the `lm object` _(to do all the different pairwise comparisons to my heart's desire)_

Let's start by loading in my data and having a look at it:

```{r data input, eval=TRUE}
#I used the original "ALL_PhysiologicalData_2015_04.txt" and added columns "Treatment" and "Merged" to it, then saved the ensuing file under "ALL_PhysiologicalData_2015_04_withMerged_Variable.txt", so I can use it for all my plots

mydata <- read.delim("ALL_PhysiologicalData_2015_04_withMerged_Variable.txt", sep="\t", header=T)

mean.df <- read.delim("Physiological_Data_Mean_Values.txt", sep="\t", header=T)

str(mydata)
```

```{r graph_Growthrate, eval=TRUE}
p <- ggplot (mydata , aes(Treatment, Growthrate.dd.1 ))
p + geom_point(aes(group=Merged, colour=Species), size = 3)+
  labs(title="", x ="")+
  geom_point(data=mean.df , aes(Treatment, Growthrate.dd.1, size=2, colour=Species), shape = 45, size = 9)+
  guides(alpha = "none", size = "none", shape = "none")

```

To really understand what we are seeing, especially with the copper data, we need to remember the different metal concentrations that are used for the different strains and treatments:

```{r tabkle metal concnetrations per treatment, eval=TRUE}
kable((read.delim("MetalConcentrationsInMedia.txt")), format = "markdown")
```

__Fe concentrations__:

If we look closely at the table above, we will see that for __both strains__, we subjected them to the __same high Fe__ concentration (__1370nmol__) and the __same low Fe__ concentration (__12.5nmol__) in the media.

__Cu concentrations - high__:

However, as per preliminary tests (_data not shown_), these two strains have different Cu requirements to sustain their respective optimal growth rates and to limit their growth rates by Cu. 
Hence, high Cu concentrations differ in the following way: __TO 1003__ requires 10.2 nmol total Cu in its growth medium under our chosen high Fe regime, whereas __TO1005__ requires more, namely __14.32 nmol total Cu__ in the control medium.

__Cu concentrations - low__:

Looking at limiting Cu concentrations, a similar scenario is seen. Where __TO 1003__ is very hard to limit with Cu, when sufficient Fe is present in the media (only background Cu is present in our study ~ __0.2 nmol Cu__), __TO 1005__ shows significant limitation at Cu levels of __6.08 nmol__. When subjected to iron / copper co-limitation, __TO 1005__ growthrate is even more limited, hinting at an interactive effect of iron and copper concentrations (which we will see further down statistically proven).
Under low Fe conditions, __TO 1003__ can not survive with only background copper concentration. Hence, we added more Cu (__1.96 nmol Cu__) under Fe-limiting conditions compared to low Cu concentrations under Fe-replete conditions (0.2 nmol). This again, shows an interdependence of Fe and Cu albeit, we don;t necessarily see it when we look at the graph, as it only states "low Cu" and "lowFeCu"without going into detail of the copper concentrations. in TO 1003, the growthrates for low Cu and low FeCu are similar so one could be misled into the interpretation that there is no real co-limitation. However, with the background information given here, it is clear that __there is also Fe-Cu-colimitation occuring in TO 1003__ (as has been shown in previous studies).

<a id="z_all"></a>

#### z_all - linear model checking for all interactions and main effects

[Back Up](#BackUP)

```{r lm growthrate_allMain and Interaction, eval=TRUE}
z_all <- lm(data=mydata, Growthrate.dd.1~(Species*Fe.level*Cu.level)) #this will model the Growth rate dependend on the 
#three main effects (Species, Fe.level, Cu.level) and will include all possible interactions
summary(z_all)

```

To look at the actual differences, we need to look at the `anova` table:

```{r lm growthrate_allMain and Interaction_ANOVA, eval=TRUE}
anova(z_all) #this will use the linear model and give us a table of the analysis of the variance in our dataset

```



Looking at the ANOVA table for the linear model that test for all main effects and interactions, we see that

* __Species__ does have a significant effect on growth rate (F (1,16) = 11.67, p.val < 0.01)
* __Fe. level__ has an effect on growthrate (F (1,16) = 35.47, p.val < 0.0001)
* __Cu level__ has an effect on growthrate (F (1,16) = 152.75, p.val < 0.00001)
* there is an __interaction__ between __Species and Fe LEVEL__ (F(1,16) = 22.47, p.val = 0.0002)
    + i.e. depending on the Species the growthrate is different under similar Fe conditions
* there is NOT INTERACTION between Species and CU LEVEL
    + i.e. this is somewhat what I had aimed for as this means that both Species have a similar growthrate reduction under the same Cu.level -> this way I can see how their proteomic and physiological response is similar or different!
* there is an __interaction__ between __Fe LEVEL and Cu LEVEL__ (F(1,16) = 8.29, p.val = 0.01) 

__NOTE:__ the anova table only tells me that there are differences e.g. between the Species. IT DOES NOT TELL ME depending on what variables etc... for that we need to do pairwise comparisons.



<a id="z"></a>

### z - linear model not checking for interaction between Cu and species 

[Back Up](#BackUP)

__FIRST THOUGH__: as we saw in the `anova` table that there is __no interaction between Cu.level and Species__, we can __take the interaction term OUT__ when we make the linear model. Let's see how this will change the model


```{r lm growthrate_allMain just known interaction, eval=TRUE}
z <- lm(data=mydata, Growthrate.dd.1~(Species+Fe.level+Cu.level)^2-Species:Cu.level) #this will model the Growth rate dependend on
#three main effects (Species, Fe.level, Cu.level) and will include 
#possible interactions between Species:Fe.level, Fe.level:Cu.level 
#but NOT Species:Cu.level as we took that one out!

summary(z)
plot(z) ##these plots are diagnostic and will give indications if the assumptions are met
```

<a id="anova_z"></a>

#### Anova table of z model

[Back Up](#BackUP)

Again, we need to look at the ANOVA table:
```{r lm growthrate_allMain limited Interaction_ANOVA, eval=TRUE}
anova(z) #this will use the linear model and give us a table of the analysis of the variance in our dataset

```


Looking at the ANOVA table for the linear model that _does not_ test for interaction between Cu.level and Species, basically, we see the same significant factors and interactions as before, just with stronger significance (probably due to the higher degrees of freedom: 18 vs 16)



* __Species__ does have a significant effect on growth rate
* __Fe. level__ has an effect on growthrate
* __Cu level__ has an effect on growthrate now: (F (1,18) = 155.27, p.val <0.00001),  [*before:(F (1,16) = 152.75, p.val <0.00001)*]
* there is still an __interaction__ between __Species and Fe LEVEL__ now: (F(1,18) = 22.84, p.val = 0.000015), [*before: (F(1,16) = 22.47, p.val = 0.0002)*]
    + i.e. depending on the Species the growthrate is different under similar Fe conditions
* there is an __interaction__ between __Fe LEVEL and Cu LEVEL__ now: (F(1,18) = 8.43, p.val < 0.01), [*before: (F(1,16) = 8.29, p.val = 0.01)*] 

### What if we use the `phia` package to look into interactions or main effects?

<a id="phia_interaction"></a>

[Back Up](#BackUP)

This is basically from the tutorial / examples given in the `R` vignette by _Helios De Rosario Martinez_ ["Analysing interactions of fitted models"](https://cran.r-project.org/web/packages/phia/vignettes/phia.pdf)

[...] In factorial experiments like this one, the dependency between factor levels and the response variable is usually represented in a contingency table, where the rows and columns are related to the different levels of both treatments, and __each cell contains the adjusted mean of the response for the corresponding interaction of factors__. When there is an interaction effect, the cell means are taken as the most straightforward way of representing this effect. 

These values and their standard errors can be obtained from the model coeffients with the function `interactionMeans` in the package `phia`, using the fitted model as first (and in this case only) argument:

```{r phia_interaction means, eval=TRUE}

(mydata.means <- interactionMeans(z))
plot(mydata.means)
```

This plot shows us main effects (such as Cu.level) and first order interactions (such as Species and Fe.level). As per the "marginality principle" (see J. A. Nelder, \A reformulation of linear models," Journal of the Royal Statistical Society. Series A (General), vol. 140, no. 1, pp. 48{77, 1977.), those factors that are involved in interactions, should not be interpreted as single effects.

As we see in the upper right and lower left corner, Species and Cu really do not seem to have an interaction effect. They change in the same way (lines are parallel). However, when we look at upper middle and middle left cell, we see that growthrate changes in a different way depending on Species and Fe level. And to a much lesser extend for Fe.level and Cu.level as seen in middle right and lower middle cell.

#### Pairwise Comparisons

<a id="phia_pairwise"></a>

[Back Up](#BackUP)

In order to put actual numbers for the significant differences, I will proceed with pairwise comparisons by having a fixed factor and testing how it changes dependend on another factor

```{r phia_interaction_Contrasts_Species_Felevel, eval=TRUE}
testInteractions(z, fixed="Species", across="Fe.level")
```

This means that the two different Fe.levels I used (high and low) do not significantly change the growth rate in TO 1003 (F(1,18) = 0.75, p.val = 0.397) but they do change the growthrate significantly in TO 1005 (F(1,18) = 58.14, p-val < 0.00001))

```{r phia_interaction_Contrasts_Fe.level_Species, eval=TRUE}
testInteractions(z, fixed="Fe.level", across="Species")
```

This means that the two species have significantly different growthrates under high Fe conditions (F(1,18), p.val < 0.0001) but are not sig different under low Fe conditions.

```{r phia_interaction_Contrasts_Fe.level_Cu.level, eval=TRUE}
testInteractions(z, fixed="Fe.level", across="Cu.level")
```

This means that there is significant growthrate changes from high Cu to low Cu in both Species (F(1,18) = 118.03, p.val < 0.00001) and that the same is true under low Fe conditions, that the additional lowering of Cu.level changes growth rates significantly (F(1,18) = 45.67, p.val < 0.00001)

```{r phia_interaction_Contrasts_Cu.level_Fe.level, eval=TRUE}
testInteractions(z, fixed="Cu.level", across="Fe.level")
```


<a id="MyMethod"></a>

### Overview of My Method to Analyze my Physiological Data

OK, after this first inital approach, I will settle for the following:

0) have a look at the graph of the actual data! :)

1) do a `linear model`, checking for all main and interacting effects:

  + `lm(response ~ Species * Fe.level * Cu.level)`
  
2) do an `anova` on this `lm` object to see the F statistics and p-values:

  + dependig on seen or not seen interactions, modify the `lm()` accordingly
  
3) then do pairwise comparisons using `phia` package to look into what is contributing how into the significant interactions seen in the `anova`

__Note__: I am using "strain" and "species" interchangeably, even though the correct term would be "strain" in the current context

<a id="Growthrate.dd"><a>

#### Growthrate - doublings per day

First a look at the graph: 

```{r graph_Growthrate.dd, eval=TRUE}
p <- ggplot (mydata , aes(Treatment, Growthrate.dd.1))
p + geom_point(aes(group=Merged, colour=Species), size = 3)+
  labs(title="Growthrate [dd-1]", x ="")+
  geom_point(data=mean.df , aes(Treatment, Growthrate.dd.1, size=2, colour=Species), shape = 45, size = 9)+
  guides(alpha = "none", size = "none", shape = "none")+
  expand_limits(y=0)

```

Now we start with a linear model testing for all main effects and interactions possible:
```{r lm_all_Growthrate.dd, eval=TRUE}
lm_all_Growthrate.dd <- lm(data = mydata, Growthrate.dd.1 ~ (Species * Fe.level * Cu.level))
summary(lm_all_Growthrate.dd) # we need to look at the actual anova to knwo where we need to look further
```

The lower three lines in this summary tell us how well the model fits to our actual data that we based the model on. 
Multiple R-squared: 0.9356 means that 93.56% of the data can be explained by/ fall within the range of  this model.
The statistical significance of this model is given as F(7,16) = 33.19, p-val = 2.274e-08.

```{r lm_all_Growthrate.dd_anova, eval=TRUE}
anova(lm_all_Growthrate.dd) # #this will use the linear model and give us a table of the analysis of the variance in our dataset
#and it shows us, we can take out the interaction between Species: Cu.level
```


Looking at the ANOVA table for the linear model that test for all main effects and interactions, we see that

* __Species__ does have a significant effect on growth rate (F (1,16) = 11.67, p.val < 0.01)
* __Fe. level__ has an effect on growthrate (F (1,16) = 35.47, p.val < 0.0001)
* __Cu level__ has an effect on growthrate (F (1,16) = 152.75, p.val < 0.00001)
* there is an __interaction__ between __Species and Fe level__ (F(1,16) = 22.47, p.val = 0.0002)
    + i.e. depending on the Species the growthrate is different under similar Fe conditions
* there is NO INTERACTION between Species and Cu level
    + i.e. this is somewhat what I had aimed for as this means that both Species have a similar growthrate reduction under the same Cu.level -> this way I can see how their proteomic and physiological response is similar or different!
* there is an __interaction__ between __Fe level and Cu level__ (F(1,16) = 8.29, p.val = 0.01) 

__NOTE:__ the anova table only tells me that there are differences e.g. between the Species. IT DOES NOT TELL ME depending on what variables etc... for that we need to do pairwise comparisons.


### linear model not checking for interaction between Cu and species 

[Back Up](#BackUP)

__FIRST THOUGH__: as we saw in the `anova` table that there is __no interaction between Cu.level and Species__, we can __take the interaction term OUT__ when we make the linear model. Let's see how this will change the model


```{r lm growthrate.dd _allMain just known interaction, eval=TRUE}
lm_Growthrate.dd <- lm(data=mydata, Growthrate.dd.1~(Species+Fe.level+Cu.level)^2-Species:Cu.level) #this will model the Growth rate dependend on
#three main effects (Species, Fe.level, Cu.level) and will include 
#possible interactions between Species:Fe.level, Fe.level:Cu.level 
#but NOT Species:Cu.level as we took that one out!

summary(lm_Growthrate.dd)
plot(lm_Growthrate.dd) ##these plots are diagnostic and will give indications if the assumptions are met
```



#### Anova table of reduced linear model

[Back Up](#BackUP)

Again, we need to look at the ANOVA table:
```{r lm growthrate.dd_allMain limited Interaction_ANOVA, eval=TRUE}
anova(lm_Growthrate.dd) #this will use the linear model and give us a table of the analysis of the variance in our dataset

```


Looking at the ANOVA table for the linear model that _does not_ test for interaction between Cu.level and Species, basically, we see the same significant factors and interactions as before, just with stronger significance (probably due to the higher degrees of freedom: 18 vs 16)



* __Species__ does have a significant effect on growth rate
* __Fe. level__ has an effect on growthrate
* __Cu level__ has an effect on growthrate now: (F (1,18) = 155.27, p.val <0.00001),  [*before:(F (1,16) = 152.75, p.val <0.00001)*]
* there is still an __interaction__ between __Species and Fe LEVEL__ now: (F(1,18) = 22.84, p.val = 0.000015), [*before: (F(1,16) = 22.47, p.val = 0.0002)*]
    + i.e. depending on the Species the growthrate is different under similar Fe conditions
* there is an __interaction__ between __Fe LEVEL and Cu LEVEL__ now: (F(1,18) = 8.43, p.val < 0.01), [*before: (F(1,16) = 8.29, p.val = 0.01)*] 

### What if we use the `phia` package to look into interactions or main effects?

[Back Up](#BackUP)

This is basically from the tutorial / examples given in the `R` vignette by _Helios De Rosario Martinez_ ["Analysing interactions of fitted models"](https://cran.r-project.org/web/packages/phia/vignettes/phia.pdf)

[...] In factorial experiments like this one, the dependency between factor levels and the response variable is usually represented in a contingency table, where the rows and columns are related to the different levels of both treatments, and __each cell contains the adjusted mean of the response for the corresponding interaction of factors__. When there is an interaction effect, the cell means are taken as the most straightforward way of representing this effect. 

These values and their standard errors can be obtained from the model coeffients with the function `interactionMeans` in the package `phia`, using the fitted model as first (and in this case only) argument:

```{r lm_Growthrate.dd_phia_interaction means, eval=TRUE}

(lm_Growthrate.dd.means <- interactionMeans(lm_Growthrate.dd))
plot(lm_Growthrate.dd.means)
```

This plot shows us main effects (such as Cu.level) and first order interactions (such as Species and Fe.level). As per the "marginality principle" (see J. A. Nelder, \A reformulation of linear models," Journal of the Royal Statistical Society. Series A (General), vol. 140, no. 1, pp. 48{77, 1977.), those factors that are involved in interactions, should not be interpreted as single effects.

As we see in the upper right and lower left corner, Species and Cu really do not seem to have an interaction effect. They change in the same way (lines are parallel). However, when we look at upper middle and middle left cell, we see that growthrate changes in a different way depending on Species and Fe level. And to a much lesser extend for Fe.level and Cu.level as seen in middle right and lower middle cell.

#### Pairwise Comparisons

<a id="phia_pairwise"></a>

[Back Up](#BackUP)

In order to put actual numbers for the significant differences, I will proceed with pairwise comparisons by having a fixed factor and testing how it changes dependend on another factor

```{r lm_Growthrate.dd_phia_interaction_Contrasts_Species_Felevel, eval=TRUE}
testInteractions(lm_Growthrate.dd, fixed="Species", across="Fe.level")
```

This means that the two different Fe.levels I used (high and low) do not significantly change the growth rate in TO 1003 (F(1,18) = 0.75, p.val = 0.397) but it does change the growthrate significantly in TO 1005 (F(1,18) = 58.14, p-val < 0.00001)).

Note, that for this, the integrated growthrates for all high Fe treatments (control and low Cu) are compared to the integrated low Fe growthrates (low Fe and low FeCu) fo the respective Specie.

```{r lm_Growthrate.dd_phia_interaction_Contrasts_Fe.level_Species, eval=TRUE}
testInteractions(lm_Growthrate.dd, fixed="Fe.level", across="Species")
```

This means that the two Species have significantly different growthrates under high Fe conditions (F(1,18), p.val < 0.0001) but are not sig different under low Fe conditions

```{r lm_Growthrate.dd_phia_interaction_Contrasts_Fe.level_Cu.level, eval=TRUE}
testInteractions(lm_Growthrate.dd, fixed="Fe.level", across="Cu.level")
```

This means that there is significant growthrate changes from high Cu to low Cu in both Species (F(1,18) = 118.03, p.val < 0.00001) and that the same is true under low Fe conditions, that the additional lowering of Cu.level changes growth ratessignificantly (F(1,18) = 45.67, p.val < 0.00001)

```{r lm_Growthrate.dd_phia_interaction_Contrasts_Cu.level_Fe.level, eval=TRUE}
testInteractions(lm_Growthrate.dd, fixed="Cu.level", across="Fe.level")
```
~~~~~~~~~~~~`



<a id="Growthrate.percent"></a>

#### Growthrate - percent of mu max

[Back Up](#BackUP)

First a look at the graph: 

```{r graph_Growthrate.percent, eval=TRUE}
p <- ggplot (mydata , aes(Treatment, Growthrate.Percent..u.umax.))
p + geom_point(aes(group=Merged, colour=Species), size = 3)+
  labs(title="", x ="")+
  geom_point(data=mean.df , aes(Treatment, Growthrate.Percent, size=2, colour=Species), shape = 45, size = 9)+
  guides(alpha = "none", size = "none", shape = "none")

```

Now we start with a linear model testing for all main effects and interactions possible:

```{r lm_all_Growthrate.percent, eval=TRUE}
lm_all_Growthrate.percent <- lm(data = mydata, Growthrate.Percent..u.umax. ~ (Species * Fe.level * Cu.level))
summary(lm_all_Growthrate.percent) # we need to look at the actual anova to knwo where we need to look further
anova(lm_all_Growthrate.percent) # this shows, we can take out the interaction between Species: Cu.level
```


```{r lm_Growthrate.percent, eval=TRUE}
lm_Growthrate.percent <- lm(data = mydata, Growthrate.Percent..u.umax. ~ (Species + Fe.level + Cu.level)^2 - Species:Cu.level)
summary(lm_Growthrate.percent) # we need to look at the actual anova to knwo where we need to look further
plot.new()
plot(lm_Growthrate.percent)

anova(lm_Growthrate.percent) # this shows, we can take out the interaction between Species: Cu.level
```

### Anova Table - Growthrate.Percent

Looking at the ANOVA table for the linear model that _does not_ test for interaction between Cu.level and Species, for the data __Growthrate Percent of umax__, we see the following significant factors:


* __Species__ is __not__ a main effect on its own
* __Fe. level__ has an effect on growthrate
* __Cu level__ has an effect on growthrate now 
* there is still an __interaction__ between __Species and Fe level now: (F(1,18) = 14.80, p.val = 0.001)
    + i.e. depending on the Species the growthrate is different under similar Fe conditions
* there is an __interaction__ between __Fe level and Cu level: (F(1,18) = 7.32, p.val = 0.02)


### Using the `phia` package to look into significant effects in growthrate percent of mu max?

Again, any main effects that are included in interacting effects will be looked at through pairwise comparisons of the interacting factors

```{r phia_interaction means_Growthrate.percent, eval=TRUE}

(Growthrate.percent.means <- interactionMeans(lm_Growthrate.percent))
plot(Growthrate.percent.means)
```

This plot shows us main effects (such as Cu.level) and first order interactions (such as Species and Fe.level). As per the "marginality principle" (see J. A. Nelder, \A reformulation of linear models," Journal of the Royal Statistical Society. Series A (General), vol. 140, no. 1, pp. 48{77, 1977.), those factors that are involved in interactions, should not be interpreted as single effects.

As we see in the upper right and lower left corner, Species and Cu really do not seem to have an interaction effect. They change in the same way (lines are parallel). However, when we look at upper middle and middle left cell, we see that growthrate changes in a different way depending on Species and Fe level. And to a much lesser extend for Fe.level and Cu.level as seen in middle right and lower middle cell.

#### Pairwise Comparisons

<a id="phia_pairwise"></a>

[Back Up](#BackUP)

In order to put actual numbers for the significant differences, I will proceed with pairwise comparisons by having a fixed factor and testing how it changes dependend on another factor

```{r phia_interaction_Contrasts_Species_Felevel_Growthrate.percent, eval=TRUE}
testInteractions(lm_Growthrate.percent, fixed="Species", across="Fe.level")
```

This means that the two different Fe.levels I used (high and low) does not significantly change the growth rate in TO 1003 (F(1,18) = 0.79, p.val = 0.39) but it does change the growthrate significantly in TO 1005 (F(1,18) = 40.05, p-val < 0.0001))

```{r phia_interaction_Contrasts_Fe.level_Species_Growthrate.percent, eval=TRUE}
testInteractions(lm_Growthrate.percent, fixed="Fe.level", across="Species")
```

This means that the two Species have no significantly different growthrates under high Fe conditions (F(1,18) = 4.02, p.val = 0.06) which makes sense as they have both umax as 100 percent and are both similarly reduced by teh given Cu.levels that they have been subjected to. Under low iron their respective growthrates are significantly different (F =  11.81, p.val = 0.006)


```{r phia_interaction_Contrasts_Fe.level_Cu.level_Growthrate.percent, eval=TRUE}
testInteractions(lm_Growthrate.percent, fixed="Fe.level", across="Cu.level")
```

This means that there is significant growthrate changes from high Cu to low Cu in both Species (F(1,18) = 99.67, p.val < 0.00001) and that the same is true under low Fe conditions, that the additional lowering of Cu.level changes growth rates significantly (F(1,18) = 37.90, p.val < 0.00001)

```{r phia_interaction_Contrasts_Cu.level_Fe.level_Growthrate.percent, eval=TRUE}
testInteractions(lm_Growthrate.percent, fixed="Cu.level", across="Fe.level")
```

This means that there is significant growth reduction under high Cu when Fe is limiting (F(1,18) = 30.49, p.val < 0.0001). However, under low Cu, the additional Fe limitation does not have a significant additional effect on growthrate. As discussed earlier, this makes sense when looking at the actual Cu concentrations used and is not in discrepancy to former studies that did find evidence of co limitation in both strains. 



<a id="FvFm"></a>

#### Fv/Fm

[Back Up](#BackUP)

First a look at the graph: 

```{r graph_FvFm, eval=TRUE}
p <- ggplot (mydata , aes(Treatment, FvFm.old))
p + geom_point(aes(group=Merged, colour=Species), size = 3)+
  labs(title="", x ="")+
  geom_point(data=mean.df , aes(Treatment, FvFm.old, size=2, colour=Species), shape = 45, size = 9)+
  guides(alpha = "none", size = "none", shape = "none")+
  expand_limits(y=0)

```

Now we start with a linear model testing for all main effects and interactions possible:

```{r lm_all_FvFm, eval=TRUE}
lm_all_FvFm <- lm(data = mydata, FvFm.old ~ (Species * Fe.level * Cu.level))
summary(lm_all_FvFm) # we need to look at the actual anova to knwo where we need to look further
anova(lm_all_FvFm) # this shows, we can take out the interaction between Species: Fe.level
```

This one shows that there is no species:Fe.level interaction. So we will take it out in our modified `lm()`:

```{r lm_FvFm, eval=TRUE}
lm_FvFm <- lm(data = mydata, FvFm.old ~ (Species + Fe.level + Cu.level)^2 - Species:Fe.level)
summary(lm_FvFm) # we need to look at the actual anova to knwo where we need to look further
plot.new()
plot(lm_FvFm)

anova(lm_FvFm) #
```

### Anova Table - FvFm

Looking at the ANOVA table for the linear model that _does not_ test for interaction between Fe.level and Species, for the data __Fv/Fm__, we see the following significant factors:


* __Species__ is  has an effect 
* __Fe. level__ has an effect 
* __Cu level__ has an effect  
* there is an __interaction__ between __Species and Cu level now: (F(1,17) = 21.37, p.val =  0.005)
* there is an __interaction__ between __Fe level and Cu level: (F(1,17) = 6.20, p.val = 0.02)


### Using the `phia` package to look into significant effects in Fv/Fm

Again, any main effects that are included in interacting effects will be looked at through pairwise comparisons of the interacting factors

```{r phia_interaction means_FvFm, eval=TRUE}

(FvFm.means <- interactionMeans(lm_FvFm))
plot(FvFm.means)
```

This plot shows us main effects (such as species in respect to Fe.level) and first order interactions (such as Species and Cu.level). As per the "marginality principle" (see J. A. Nelder, \A reformulation of linear models," Journal of the Royal Statistical Society. Series A (General), vol. 140, no. 1, pp. 48{77, 1977.), those factors that are involved in interactions, should not be interpreted as single effects.

As we see in the upper right and lower left corner, Species and Cu  seem to have an interaction effect. Fv/Fm changes differently from high Cu to low Cu in the two species. When we look at upper middle and middle left cell, we see that Fv/Fm changes in the same way for both species in response to the same high/low Fe concentrations. This is particularly interesting as we used different Cu concentrations. This would suggest that the two strains have both started their physiological response to low iron in a similar way even though the growthrate changes do not reflect this! The interplay between Fe.level and Cu.level is seen in the middle right and lower middle cell.

#### Pairwise Comparisons

[Back Up](#BackUP)

In order to put actual numbers for the significant differences, I will proceed with pairwise comparisons by having a fixed factor and testing how it changes dependend on another factor

```{r phia_interaction_Contrasts_Species_Felevel_FvFm, eval=TRUE}
testInteractions(lm_FvFm, fixed="Species", across="Cu.level")
```

This means that the two different Cu.levels I used (high and low) does significantly change Fv/Fm in TO 1003 (F(1,17) = 32.10, p.val < 0.0001) but it does not change Fv/Fm significantly in TO 1005 (F(1,17) = 1.32, p-val > 0.2))

```{r phia_interaction_Contrasts_Fe.level_Species_FvFm, eval=TRUE}
testInteractions(lm_FvFm, fixed="Cu.level", across="Species")
```

This means that the two Species have slightly significantly different Fv/Fm under high Cu conditions (F(1,17) = 8.12, p.val = 0.01). Looking at the graph, they have almost the same Fv/Fm under control condition. However, under lowFe (which is the other high Cu condition), their Fv/Fm is sufficiently different to generate the p.val = 0.01. This could mean that TO 1003 has a more pronounced low iron response (again, even though this is not reflected at all in its growthrate decrease).

Under low Cu conditions, Fv/Fm is markedly different between the two strains (F = 61.27, p.val < 0.00001).


```{r phia_interaction_Contrasts_Fe.level_Cu.level_FvFm, eval=TRUE}
testInteractions(lm_FvFm, fixed="Fe.level", across="Cu.level")
```

This means that there is significant changes in Fv/Fm from high Cu to low Cu when integrated over both strains (F(1,17) = 25.96, p.val = 0.0002). This is likely mainly influenced by the very strong difference in TO 1003. 
WHen looking at low Fe and changing Cu from high to low, the difference in Fv/Fm is not significant anymore (F (1,17) = 3.07, pval = 0.1)

```{r phia_interaction_Contrasts_Cu.level_Fe.level_FvFm, eval=TRUE}
testInteractions(lm_FvFm, fixed="Cu.level", across="Fe.level")
```

This means that there is significant reduction in Fv/Fm across both species under high Cu when Fe is limiting (F(1,17) = 27.57, p.val = 0.0001). However, under low Cu, the additional Fe limitation does not have a significant additional effect on Fv/Fm.


<a id="Sigma"></a>

#### Sigma

[Back Up](#BackUP)

First a look at the graph: 

```{r graph_Sigma, eval=TRUE}
p <- ggplot (mydata , aes(Treatment, Sig.old))
p + geom_point(aes(group=Merged, colour=Species), size = 3)+
  labs(title="", x ="")+
  geom_point(data=mean.df , aes(Treatment, Sig.old, size=2, colour=Species), shape = 45, size = 9)+
  guides(alpha = "none", size = "none", shape = "none")+
  expand_limits(y=0)

```

Now we start with a linear model testing for all main effects and interactions possible:

```{r lm_all_Sigma, eval=TRUE}
lm_all_Sigma <- lm(data = mydata, Sig.old ~ (Species * Fe.level * Cu.level))
summary(lm_all_Sigma) # we need to look at the actual anova to knwo where we need to look further
anova(lm_all_Sigma) # this shows, we can take out the interaction between Species: Cu.level
```

There seems to be no Fe.level : Cu.level interaction. So, let's take it out in this `lm()`:

```{r lm_Sigma, eval=TRUE}
lm_Sigma <- lm(data = mydata, Sig.old ~ (Species + Fe.level + Cu.level)^2 - Fe.level:Cu.level)
summary(lm_Sigma) # we need to look at the actual anova to knwo where we need to look further
plot.new()
plot(lm_Sigma)

anova(lm_Sigma) # this shows, we can take out the interaction between Species: Cu.level
```

### Anova Table - Sigma

Looking at the ANOVA table for the linear model that _does not_ test for interaction between Cu.level and Species, for the data __Growthrate Percent of umax__, we see the following significant factors:


* __Species__ is __not__ has an effect
* __Fe. level__ has an effect 
* __Cu level__ has an effect 
* there is  an __interaction__ between __Species and Fe level now: (F(1,14) = 13.36, p.val = 0.003)
* there is a strong __interaction__ between __Species and Cu level: (F(1,14) = 49.09, p.val < 0.00001)


### Using the `phia` package to look into significant effects regarding SIGMA

Again, any main effects that are included in interacting effects will be looked at through pairwise comparisons of the interacting factors

```{r phia_interaction means_Sigma, eval=TRUE}

(Sigma.means <- interactionMeans(lm_Sigma))
plot(Sigma.means)
```

This plot shows us main effects (such as Cu.level in regards to Fe.level) and first order interactions (such as Species and Fe.level). As per the "marginality principle" (see J. A. Nelder, \A reformulation of linear models," Journal of the Royal Statistical Society. Series A (General), vol. 140, no. 1, pp. 48{77, 1977.), those factors that are involved in interactions, should not be interpreted as single effects.

As we see in the upper right and lower left corner, Species and Cu really do seem to have very different results for Sigma.  Whenhen we look at upper middle and middle left cell, we see that Sigma also changes in a different way depending on Species and Fe level.  Differing Fe.level and Cu.level seem to change sigma in a comparable fashion.

#### Pairwise Comparisons

[Back Up](#BackUP)

In order to put actual numbers for the significant differences, I will proceed with pairwise comparisons by having a fixed factor and testing how it changes dependend on another factor

```{r phia_interaction_Contrasts_Species_Felevel_Sigma, eval=TRUE}
testInteractions(lm_Sigma, fixed="Species", across="Fe.level")
```

This means that the two different Fe.levels I used (high and low) does not significantly change Sigma in TO 1003 (F(1,14) = 2.54, p.val = 0.13) but it does change Sigma significantly in TO 1005 (F(1,14) = 41.73, p-val < 0.0001)

```{r phia_interaction_Contrasts_Fe.level_Species_Sigma, eval=TRUE}
testInteractions(lm_Sigma, fixed="Fe.level", across="Species")
```

This means that the two Species have significantly different Sigma when integrated over their respective high Fe conditions (F(1,14) = 25.26, p.val = 0.0004).
Under low iron their respective Sigmas are statistically almost the same (F (1,14) =  0, p.val = .999). Which makes sense when you look at the graph. Even though the trends are the same (i.e. under low Fe and lowFeCu, TO 1005 stays the same, whereas TO 1003 increases its Sigma). But because the unchanged Sigma of TO 1005 sits right int he middle of the low and high Sigma values of TO 1003, their integrated fixed low Fe values are the same.


```{r phia_interaction_Contrasts_Fe.level_Cu.level_Sigma, eval=TRUE}
testInteractions(lm_Sigma, fixed="Species", across="Cu.level")
```

Here, TO 1003 has a very strong Cu-effect (F(1,14) = 112.72, pval < 0.00001).
WHereas, Cu doesn;t seem to have any effect on Sigma for TO 1005 (F(1,14) = 0.02, pval = 0.88).


```{r phia_interaction_Contrasts_Cu.level_Fe.level_Sigma, eval=TRUE}
testInteractions(lm_Sigma, fixed="Cu.level", across="Species")
```

Under high Cu treatments (i.e. as response to low Fe only), the two strains show somewhat significant differences (F(1,14) = 4.89, p.val = 0.04). This is due to starting witht he same Sigma in the control treatment. THen TO 1003 shows almost no response to low Fe but TO 1005 does show a significant response to Fe. Hence, the differnece between the two strains is significant. 

This difference between the strains is even more pronounced when looking at the low Cu treatments (F (1,14) = 64.01, p.val = 0.00001). Here, TO 1003 shows almost no reponse to an added FeCu co- limitation, whereas Sigma in TO 1005 does increase significantly from low Cu to low CuFe co-limitation 


###Summary SIGMA

There are strong significant differences between TO 1003 and TO 1005 how their SIGMA changes in response to Fe, Cu, or Fe-Cu co-limitation:

__Sigma__ in __TO 1003 does not respond to lowering Fe concentrations__ (neither low Fe alone compared to high Fe, nor low FeCu compared to low Cu)

Completely diametrically different to its sister strain!!!!

__Sigma__ in __TO 1005 does not respond to lowering Cu concentrations__ (neither low Cu alone compared to high Cu, nor low FeCu compared to low Fe)

<a id="PQ"></a>

#### PQ

[Back Up](#BackUP)

First a look at the graph: 

```{r graph_PQ, eval=TRUE}
p <- ggplot (mydata , aes(Treatment, PQ_Siz.old))
p + geom_point(aes(group=Merged, colour=Species), size = 3)+
  labs(title="PQ_Size", x ="")+
  geom_point(data=mean.df , aes(Treatment, PQ_Siz.old, size=2, colour=Species), shape = 45, size = 9)+
  guides(alpha = "none", size = "none", shape = "none")+
  expand_limits(y=0)
#I double checked the excel summary file I got from Nina for the "0" value in TO 1003 low Fe (B) treatment. All other values (Fv/Fm, Sigma, p, tau seem to be in the same league as the other two biological replicates... might have to double chekc with Nina, if she has some thoughts on what happened with PQ_size, here)
```

Now we start with a linear model testing for all main effects and interactions possible:

```{r lm_all_PQ, eval=TRUE}
lm_all_PQ <- lm(data = mydata, PQ_Siz.old ~ (Species * Fe.level * Cu.level))
summary(lm_all_PQ) # we need to look at the actual anova to knwo where we need to look further
anova(lm_all_PQ) # this shows, we can take out the interaction between Species: Cu.level
```

There seems to be no Fe.level : Cu.level interaction, and no Species:Cu.level interaction. So, first let's take  them out in this `lm()`:

```{r lm_PQ, eval=TRUE}
lm_PQ <- lm(data = mydata, PQ_Siz.old ~ (Species + Fe.level + Cu.level)^2 - Fe.level:Cu.level - Species:Fe.level)
summary(lm_PQ) # we need to look at the actual anova to knwo where we need to look further
plot.new()
plot(lm_PQ)

anova(lm_PQ) # this shows, we can take out the interaction between Species: Cu.level
```

### Anova Table - PQ

Looking at the ANOVA table for the linear model that _does not_ test for interaction between Fe.level : Cu.level interaction or Species : Fe.level, for the data __PQ_Size__, we see the following significant factors:


* __Species__ alone has __not__ an effect
* __Fe. level__ alone has a significant effect (F(1,15), p.val = 0.025) 
* __Cu level__ alone has __not__ an effect
* there is  an __interaction__ between __Species and Cu level now: (F(1,15) = 7.71, p.val = 0.01)



### Using the `phia` package to look into significant effects regarding PQ

Again, any main effects that are included in interacting effects will be looked at through pairwise comparisons of the interacting factors

```{r phia_interaction means_PQ, eval=TRUE}

(PQ.means <- interactionMeans(lm_PQ))
plot(PQ.means)
```

This plot shows us the main effect (i.e. Fe.level) and first order interactions (such as Species and Cu.level). As per the "marginality principle" (see J. A. Nelder, \A reformulation of linear models," Journal of the Royal Statistical Society. Series A (General), vol. 140, no. 1, pp. 48{77, 1977.), those factors that are involved in interactions, should not be interpreted as single effects.

As we see in the upper right and lower left corner, Species and Cu really do seem to have very different results for PQ.  When we look at upper middle and middle left cell, we see that PQ  changes in a very similar way for both species in response to Fe.level adn that this response is to reduce the PQ.size. Differing Fe.level and Cu.level seem to change PQ in a comparable fashion (middle right and lower middle).

#### Pairwise Comparisons

[Back Up](#BackUP)

In order to put actual numbers for the significant differences, I will proceed with pairwise comparisons by having a fixed factor and testing how it changes dependend on another factor

```{r phia_interaction_Contrasts_Species_Culevel_PQ, eval=TRUE}
testInteractions(lm_PQ, fixed="Species", across="Cu.level")
```

This means that the two different Cu.levels I used (high and low) does significantly change PQ in TO 1003 (F(1,15) = 8.01, p.val = 0.025) but it does not change PQ significantly in TO 1005 (F(1,15) = 1.43, p-val = 0.25)

```{r phia_interaction_Contrasts_Cu.level_Species_PQ, eval=TRUE}
testInteractions(lm_PQ, fixed="Cu.level", across="Species")
```

This means that the two Species have not significantly different PQ when integrated over their respective high Cu conditions (F(1,15) = 2.38, p.val = 0.14).
Under low copper their respective PQs are somewhat different (F(1, 15) = 5.99, p.val = 0.055)



###Summary PQ

There is a statistically significant __Fe effect__: lowering iron leads to lower PQ.size

Then there is an interaction effect __Species : Cu.level__:

__PQ__ in __TO 1003 statistically increases in response to lowering Cu concentrations__ (neither low Fe alone compared to high Fe, nor low FeCu compared to low Cu)

Somewhat diametrically different to its sister strain:

__PQ__ in __TO 1005 tends to decrease (not stat.) in response to lowering Cu concentrations__ 



<a id="Chla"></a>

#### Chla per cell volume __HAVE TO HAVE ANOTHER LOOK AT THREE WAY INTERACTION TESTING!!!__

[Back Up](#BackUP)

First a look at the graph: 

```{r graph_Chla, eval=TRUE}
p <- ggplot (mydata , aes(Treatment, Chla.per.cell.vol.fg.fL))
p + geom_point(aes(group=Merged, colour=Species), size = 3)+
  labs(title="Chl a / Cell vol [fg/fL]", x ="")+
  geom_point(data=mean.df , aes(Treatment, Chla.per.cell.vol.fg.fL, size=2, colour=Species), shape = 45, size = 9)+
  guides(alpha = "none", size = "none", shape = "none")+
  expand_limits(y=0)
#I double checked the excel summary file I got from Nina for the "0" value in TO 1003 low Fe (B) treatment. All other values (Fv/Fm, Sigma, p, tau seem to be in the same league as the other two biological replicates... might have to double chekc with Nina, if she has some thoughts on what happened with Chla_size, here)
```


Now we start with a linear model testing for all main effects and interactions possible:

```{r lm_all_Chla, eval=TRUE}
lm_all_Chla <- lm(data = mydata, Chla.per.cell.vol.fg.fL ~ (Species * Fe.level * Cu.level))
summary(lm_all_Chla) # we need to look at the actual anova to knwo where we need to look further
anova(lm_all_Chla) # this shows, we can take out the interaction between Species: Cu.level
```

There seems to be no Species: Fe.level and no Species: Cu.level interaction. However, there seems to be a three way species:Fe.level:Cu,level interaction. So I will not take out anything for the following analysis.


```{r lm_Chla, eval=TRUE}
lm_Chla <- lm (data = mydata, Chla.per.cell.vol.fg.fL ~ (Species * Fe.level * Cu.level)) # Yes, this is the same as before. I leave it as is
summary(lm_Chla) # we need to look at the actual anova to knwo where we need to look further
plot.new()
plot(lm_Chla)

anova(lm_Chla)
```

### Anova Table - Chla

Looking at the ANOVA table for the linear model that _does not_ test for interaction between Fe.level : Cu.level interaction or Species : Fe.level, for the data __Chla_Size__, we see the following significant factors:


* __Species__ alone has a significant effect
* __Fe. level__ alone has a significant effect  
* __Cu level__ alone has __not__ an effect
* there is  an __interaction__ between __Cu level and Fe level__ 
* there is a __3-way interaction__ between __Species, Cu level and Fe level__ (F(1, 16) = 31.42, p-val < 0.0001)



### Using the `phia` package to look into significant effects regarding Chla

Again, any main effects that are included in interacting effects will be looked at through pairwise comparisons of the interacting factors

```{r phia_interaction means_Chla, eval=TRUE}

(Chla.means <- interactionMeans(lm_Chla))
plot(Chla.means)
```

This plot shows us the main effects (no single main effects here) and first order interactions (such as Species , Cu.level, Fe. level). As per the "marginality principle" (see J. A. Nelder, \A reformulation of linear models," Journal of the Royal Statistical Society. Series A (General), vol. 140, no. 1, pp. 48{77, 1977.), those factors that are involved in interactions, should not be interpreted as single effects.

Not sure how to look at three-way interactions in this plot. But you do see the Fe:Cu level interaction when looking at middle right and lower middle. Chla concentration per cell volume changes differently depending on Fe and Cu levels. 

#### Pairwise Comparisons

[Back Up](#BackUP)

In order to put actual numbers for the significant differences in the 3-way interaction between __Species, Cu level and Fe level__, I will proceed with pairwise comparisons by having __two fixed factors__ and testing how Chl a changes dependend on the remaining factor



First: Species against Fe + Cu level
```{r phia_interaction_Contrasts_Species_CuandFelevel_Chla, eval=TRUE}
testInteractions(lm_Chla, fixed="Species", across=c("Cu.level", "Fe.level"))
```

This means that there is an Fe:Cu interaction for TO 1003 but not for TO 1005 (F( 1, 16) = 40.87, p-val < 0.0001)

Now let's see how everything plays out in more detail by fixing SPecies and Cu level and change Fe. level:

```{r phia_interaction_Contrasts_Species_and_Cu_against_Felevel_Chla, eval=TRUE}
testInteractions(lm_Chla, fixed=c("Species", "Cu.level"), across="Fe.level")
```

Control to low Fe is only significant for TO 1005 (F(1, 16) = 14.43, p-val = 0.005) but not significant for TO 1003

However, when comparing low Cu to low FeCu treatment, Chl a is only significantly reduced in TO 1003 (F(1, 16) = 72.42, p-val < 0.00001) 

```{r phia_interaction_Contrasts_Species_and_Fe_against_Culevel_Chla, eval=TRUE}
testInteractions(lm_Chla, fixed=c("Species", "Fe.level"), across="Cu.level")
```

Control to low Cu is only significant for TO 1003 (F(1, 16) = 35.49, p-val < 0.0001) but not significant for TO 1005

When comparing low Fe to low FeCu treatment, again, Chl a is only significantly reduced in TO 1003 (F(1, 16) = 9.51, p-val = 0.02) 

```{r phia_interaction_Contrasts_Cu_and_Fe_against_Species_Chla, eval=TRUE}
testInteractions(lm_Chla, fixed=c("Cu.level", "Fe.level"), across="Species")
```

Under the control treatment, both strains have the same Chl a concentration. 

Under low Cu, TO 1003 has significantly higher CHl a per Cell volume compared to TO 1005 (F(1, 16) = 49.27, p-val < 0.0001). In TO 1005 Chla stays the same compared to the control treatment.

Under low Fe, TO 1005 has significantly lower CHl a per Cell volume compared to TO 1003 (F(1, 16) = 19.78, p-val = 0.001). In TO 1003 Chla stays the same compared to the control treatment.

When co-limited (low FeCu), both strains have again the same Chl a concentration


###Summary Chla per Cell vol

Under the control treatment, both strains have the same Chl a concentration. 

Under low Cu, TO 1003 has significantly higher Chl a (+ 3.07 fg/fL) compared to the control treatment (F(1, 16) = 35.49, p-val < 0.0001), whereas Chl a concentration stays the same for TO 1005. Consequently, TO 1003 and TO 1005 have significantly different Chl a concentrations under low Cu treatment (TO 1003 has ~  + 3.61 fg/fL more Chla per cell vol compared to TO 1005) (F(1, 16) = 49.27, p-val < 0.0001). 
 
Under low Fe, the Chla per cell volume stays constant in TO 1003 compared to the control. Here, Chl a changes only in TO 1005. It decreases significantly (- 1.96 fg/fL)(F(1, 16) = 14.43, p-val = 0.005). Consequently, the difference between the two strains is also significant with F(1, 16) = 19.78 and p-val = 0.001.

When co-limited (low FeCu), both strains have again the same Chl a concentration




<a id="Chla.cell"></a>

#### Chla per cell

[Back Up](#BackUP)

First a look at the graph: 

```{r graph_Chla.cell, eval=TRUE}
p <- ggplot (mydata , aes(Treatment, Chla.per.cell.pg.cell))
p + geom_point(aes(group=Merged, colour=Species), size = 3)+
  labs(title="Chl a / Cell  [pg/cell]", x ="")+
  geom_point(data=mean.df , aes(Treatment, Chla.per.cell.pg.cell, size=2, colour=Species), shape = 45, size = 9)+
  guides(alpha = "none", size = "none", shape = "none")+
  expand_limits(y=0)

```


Now we start with a linear model testing for all main effects and interactions possible:

```{r lm_all_Chla.cell, eval=TRUE}
lm_all_Chla.cell <- lm(data = mydata, Chla.per.cell.pg.cell ~ (Species * Fe.level * Cu.level))
summary(lm_all_Chla.cell) # we need to look at the actual anova to knwo where we need to look further
anova(lm_all_Chla.cell) # this shows, we can take out the interaction between Species: Cu.level
```

There seems to be no Species: Fe.level and no Species: Cu.level interaction. However, there seems to be a three way species:Fe.level:Cu,level interaction. So I will not take out anything for the following analysis.


```{r lm_Chla.cell, eval=TRUE}
lm_Chla.cell <- lm (data = mydata, Chla.per.cell.pg.cell ~ (Species * Fe.level * Cu.level)) # Yes, this is the same as before. I leave it as is
summary(lm_Chla.cell) # we need to look at the actual anova to knwo where we need to look further
plot.new()
plot(lm_Chla.cell)

anova(lm_Chla.cell)
```

### Anova Table - Chla.cell

Looking at the ANOVA table for the linear model that _ we see the following significant factors:


* __Species__ alone has a significant effect
* __Fe. level__ alone has a significant effect  
* __Cu level__ alone has an effect
* there is  __almost__ an __interaction__ between __Species and Fe level__ 
* there is a __3-way interaction__ between __Species, Cu level and Fe level__ (F(1, 16) = 31.42, p-val < 0.0001)



### Using the `phia` package to look into significant effects regarding Chla.cell

Again, any main effects that are included in interacting effects will be looked at through pairwise comparisons of the interacting factors

```{r phia_interaction means_Chla.cell, eval=TRUE}

(Chla.cell.means <- interactionMeans(lm_Chla.cell))
plot(Chla.cell.means)
```

This plot shows us the main effects (no single main effects here) and first order interactions (such as Species , Cu.level, Fe. level). As per the "marginality principle" (see J. A. Nelder, \A reformulation of linear models," Journal of the Royal Statistical Society. Series A (General), vol. 140, no. 1, pp. 48{77, 1977.), those factors that are involved in interactions, should not be interpreted as single effects.

Not sure how to look at three-way interactions in this plot. But you do see the Fe:Cu level interaction when looking at middle right and lower middle. Chla concentration per cell  changes differently depending on Fe and Cu levels. 

#### Pairwise Comparisons

[Back Up](#BackUP)

In order to put actual numbers for the significant differences in the 3-way interaction between __Species, Cu level and Fe level__, I will proceed with pairwise comparisons by having __two fixed factors__ and testing how Chl a changes dependend on the remaining factor



First: Species against Fe + Cu level
```{r phia_interaction_Contrasts_Species_CuandFelevel_Chla.cell, eval=TRUE}
testInteractions(lm_Chla.cell, fixed="Species", across=c("Cu.level", "Fe.level"))
```

This means that there is an Fe:Cu interaction for TO 1003 but only a hint of interaction for TO 1005 (F( 1, 16) = 14.97, p-val < 0.003 for TO 1003)

Now let's see how everything plays out in more detail by fixing Species and Cu level and change Fe. level:

```{r phia_interaction_Contrasts_Species_and_Cu_against_Felevel_Chla.cell, eval=TRUE}
testInteractions(lm_Chla.cell, fixed=c("Species", "Cu.level"), across="Fe.level")
```

Control to low Fe is again (as in Chl a per cell vol) only significant for TO 1005 (F(1, 16) = 20.52, p-val = 0.001) but not significant for TO 1003

However, when comparing low Cu to low FeCu treatment, Chl a (again) is only significantly reduced in TO 1003 (F(1, 16) = 15.34, p-val = 0.004) 

```{r phia_interaction_Contrasts_Species_and_Fe_against_Culevel_Chla.cell, eval=TRUE}
testInteractions(lm_Chla.cell, fixed=c("Species", "Fe.level"), across="Cu.level")
```

Control to low Cu looks different compared to Chl a per cell volume. This time, TO 1003 is NOT significantly sifferent. Additionally, this time, TO 1005 has almost sig decreased (F(1, 16) = 7.11, p-val = 0.05) 

When comparing low Fe to low FeCu treatment, Chl a follows the trend set by Chl a per cell vol: it changes only significantly in TO 1003 (F(1, 16) = 20.45, p-val = 0.001) 

```{r phia_interaction_Contrasts_Cu_and_Fe_against_Species_Chla.cell, eval=TRUE}
testInteractions(lm_Chla.cell, fixed=c("Cu.level", "Fe.level"), across="Species")
```

Under the control treatment, both strains have comparable Chl a per cell concentrations. 

Under low Cu, TO 1003 has slightly higher Chl a per Cell  compared to TO 1005 (F(1, 16) = 6.17, p-val = 0.07). 

Compabarble to Chla per cell volumne, under low Fe, TO 1003 has significantly higher CHl a per Cell  compared to TO 1005 (F(1, 16) = 24.54, p-val < 0.001). In TO 1003 Chla per cell increases slightly compared to its control treatment, whereas TO 1005 decreases significantly compared to its control treatment.

When co-limited (low FeCu), both strains have again comparable Chl a concentration per cell.


###Summary Chla per Cell






<a id="cellsize"></a>

#### Cell Size

[Back Up](#BackUP)

First a look at the graph: 

```{r graph_cell.size, eval=TRUE}
p <- ggplot (mydata , aes(Treatment, cell.size..um))
p + geom_point(aes(group=Merged, colour=Species), size = 3)+
  labs(title="Cell Size [um]", x ="")+
  geom_point(data=mean.df , aes(Treatment, cell.size..um, size=2, colour=Species), shape = 45, size = 9)+
  guides(alpha = "none", size = "none", shape = "none")+
  expand_limits(y=0)

```


Now we start with a linear model testing for all main effects and interactions possible:

```{r lm_all_cell.size, eval=TRUE}
lm_all_cell.size <- lm(data = mydata, cell.size..um ~ (Species * Fe.level * Cu.level))
summary(lm_all_cell.size) # we need to look at the actual anova to know where we need to look further
anova(lm_all_cell.size) 
```

There seems to be no *Species : Cu.level* and no *Fe.level : Cu.level* interaction. Hence, we will take these interactions out in the next linear model:

```{r lm_cell.size, eval=TRUE}
lm_cell.size <- lm (data = mydata, cell.size..um ~ (Species + Fe.level + Cu.level)^2 - Species:Cu.level - Fe.level:Cu.level)

summary(lm_cell.size) # we need to look at the actual anova to knwo where we need to look further
plot.new()
plot(lm_cell.size)

anova(lm_cell.size)
```

### Anova Table - cell.size

Looking at the ANOVA table for the linear model that _does not_ test for interactions between Fe.level : Cu.level or Species : Fe.level, for the data __cell.Size__, we see the following significant factors:


* __Species__ alone has no significant effect
* __Fe. level__ alone has a significant effect  
* __Cu level__ alone has a significant effect (F (1, 19) = 54.32, p-val < 0.00001)
* there is  an __interaction__ between __Species and Fe level__ (F (1, 19) = 9.08, p-val = 0.007)



### Using the `phia` package to look into significant effects regarding cell.size

Again, any main effects ( here Cu. level) that are included in interacting effects will be looked at through pairwise comparisons of the interacting factors

```{r phia_interaction means_cell.size, eval=TRUE}

(cell.size.means <- interactionMeans(lm_cell.size))
plot(cell.size.means)
```

This plot shows us the main effects (here Cu level) and first order interactions (here Species : Fe level). As per the "marginality principle" (see J. A. Nelder, "A reformulation of linear models," Journal of the Royal Statistical Society. Series A (General), vol. 140, no. 1, pp. 48{77, 1977.), those factors that are involved in interactions, should not be interpreted as single effects.


#### Pairwise Comparisons

[Back Up](#BackUP)

In order to put actual numbers for the significant differences, I will do pairwise comparisons



First: Species against Fe + Cu level
```{r phia_interaction_Contrasts_Species_Felevel_cell.size, eval=TRUE}
testInteractions(lm_cell.size, fixed="Species", across="Fe.level")
```

This means that there is no statistical difference in the cell size in TO 1003 when comparing the integrated high Fe vs low Fe results.
Whereas, the cell size decreases in repsonse to low Fe in TO 1005 (F(1, 19) = 13.83, p-val = 0.003)

```{r phia_interaction_Contrasts_Felevel_and_Species_cell.size, eval=TRUE}
testInteractions(lm_cell.size, fixed = "Fe.level", across="Species")
```
This means that under high Fe conditions (control and low Cu), cell size stays the same in TO 1003 compared to TO 1005.

Under low Fe conditions there is significant differences in size between the two strains (F(1, 19) = 8.04, p-val = 0.02)


###Summary Cell Size

Low Cu decreases cell size significantly across the dataset (F(1,19) = 54.31, p-val = < 0.00001)

Under low Fe conditions, strains react differently. Cell size decreases significatnly in TO 1005 but not in TO 1003. Hence cell size is different under low Fe for the two strains (i.e. TO 1005 is smaller compared to TO 1003).



<a id="cellvol"></a>

#### Cell Volume (fl/cell)

[Back Up](#BackUP)

First a look at the graph: 

```{r graph_cell.vol, eval=TRUE}
p <- ggplot (mydata , aes(Treatment, cell.volume.fl.cell))
p + geom_point(aes(group=Merged, colour=Species), size = 3)+
  labs(title="Cell volume [fl/cell]", x ="")+
  geom_point(data=mean.df , aes(Treatment, cell.volume.fl.cell, size=2, colour=Species), shape = 45, size = 9)+
  guides(alpha = "none", size = "none", shape = "none")+
  expand_limits(y=0)

```


Now we start with a linear model testing for all main effects and interactions possible:

```{r lm_all_cell.vol, eval=TRUE}
lm_all_cell.vol <- lm(data = mydata, cell.volume.fl.cell ~ (Species * Fe.level * Cu.level))
summary(lm_all_cell.vol) # we need to look at the actual anova to know where we need to look further
anova(lm_all_cell.vol) 
```

There seems to be no *Species : Cu.level* and no *Fe.level : Cu.level* interaction. Hence, we will take these interactions out in the next linear model:

```{r lm_cell.vol, eval=TRUE}
lm_cell.vol <- lm (data = mydata, cell.volume.fl.cell ~ (Species + Fe.level + Cu.level)^2 - Species:Cu.level - Fe.level:Cu.level)

summary(lm_cell.vol) # we need to look at the actual anova to knwo where we need to look further
plot.new()
plot(lm_cell.vol)

anova(lm_cell.vol)
```

### Anova Table - cell.vol

Looking at the ANOVA table for the linear model that _does not_ test for interactions between Fe.level : Cu.level or Species : Cu.level, for the data __cell.vol__, we see the following significant factors:


* __Species__ alone has no significant effect
* __Fe. level__ alone has a significant effect  
* __Cu level__ alone has a significant effect (F (1, 19) = 47.17, p-val < 0.00001)
* there is  an __interaction__ between __Species and Fe level__ (F (1, 19) = 9.06, p-val = 0.007)



### Using the `phia` package to look into significant effects regarding cell.vol

Again, any main effects ( here Cu. level) that are included in interacting effects will be looked at through pairwise comparisons of the interacting factors

```{r phia_interaction means_cell.vol, eval=TRUE}

(cell.vol.means <- interactionMeans(lm_cell.vol))
plot(cell.vol.means)
```

This plot shows us the main effects (here Cu level) and first order interactions (here Species : Fe level). As per the "marginality principle" (see J. A. Nelder, "A reformulation of linear models," Journal of the Royal Statistical Society. Series A (General), vol. 140, no. 1, pp. 48{77, 1977.), those factors that are involved in interactions, should not be interpreted as single effects.

Integrated over high copper, cell volume is comparable for both species. The same is true for integrated low copper cell volume. However, comparing low copper to high copper treatments, there is significant difference in cell volume. Namely, cell volume decreases significantly in both species in a comparable manner. 

#### Pairwise Comparisons

[Back Up](#BackUP)

In order to put actual numbers for the significant differences, I will do pairwise comparisons



First: Species against Fe + Cu level
```{r phia_interaction_Contrasts_Species_Felevel_cell.vol, eval=TRUE}
testInteractions(lm_cell.vol, fixed="Species", across="Fe.level")
```

This means that there is no statistical difference in the cell vol in TO 1003 when comparing the integrated high Fe vs low Fe results 
Whereas, the cell size decreases in repsonse to low Fe in TO 1005 (F(1, 19) = 13.48, p-val = 0.003)

```{r phia_interaction_Contrasts_Felevel_and_Species_cell.vol, eval=TRUE}
testInteractions(lm_cell.vol, fixed = "Fe.level", across="Species")
```
This means that under high Fe conditions (control and low Cu), cell size stays the same in TO 1003 compared to TO 1005.

Under low Fe conditions there is significant differences in size between the two strains (F(1, 19) = 8.04, p-val = 0.02)


###Summary Cell Size

Low Cu decreases cell size significantly across the dataset (F(1,19) = 47.17, p-val = < 0.00001)

Under low Fe conditions, strains react differently. Cell size decreases significatnly in TO 1005 but not in TO 1003. Hence cell size is different under low Fe for the two strains (i.e. TO 1005 is smaller compared to TO 1003).




<a id="FeDFB.cell"></a>

#### FeDFB uptake per cell

[Back Up](#BackUP)

First a look at the graph: 

```{r graph_FeDFB.cell, eval=TRUE}
p <- ggplot (mydata , aes(Treatment, FeDFB.zmol.cell.1.h.))
p + geom_point(aes(group=Merged, colour=Species), size = 3)+
  labs(title="Fe DFB uptake [zmol/cell * h]", x ="")+
  geom_point(data=mean.df , aes(Treatment, FeDFB.zmol.cell.1.h., size=2, colour=Species), shape = 45, size = 9)+
  guides(alpha = "none", size = "none", shape = "none")+
  expand_limits(y=0)

```

Now we start with a linear model testing for all main effects and interactions possible:

```{r lm_all_FeDFB.cell, eval=TRUE}
lm_all_FeDFB.cell <- lm(data = mydata, FeDFB.zmol.cell.1.h. ~ (Species * Fe.level * Cu.level))
summary(lm_all_FeDFB.cell) # we need to look at the actual anova to know where we need to look further
anova(lm_all_FeDFB.cell) 
```

There seems to be *Species : Fe.level* and  *Species : Cu.level* and *Fe.level : Cu.level* interaction. Hence, we will leave all these interactions in:

```{r lm_FeDFB.cell, eval=TRUE}
lm_FeDFB.cell <- lm (data = mydata, FeDFB.zmol.cell.1.h. ~ (Species * Fe.level * Cu.level))

summary(lm_FeDFB.cell) # we need to look at the actual anova to knwo where we need to look further
plot.new()
plot(lm_FeDFB.cell)

anova(lm_FeDFB.cell)
```

### Anova Table - FeDFB.cell

Looking at the ANOVA table for the linear model that tests for all interactionsfor the data __FeDFB.cell__, we see the following significant factors:


* __Species__ alone has a significant effect
* __Fe. level__ alone has a significant effect  
* __Cu level__ alone has no significant effect 
* there is  an __interaction__ between __Species and Fe level__ (F (1, 14) = 6.52, p-val = 0.02)
* there is  an __interaction__ between __Species and Cu level__ (F (1, 14) = 6.20, p-val = 0.03)
* there is  an __interaction__ between __Fe level and Cu level__ (F (1, 14) = 17.67, p-val < 0.001)



### Using the `phia` package to look into significant effects regarding FeDFB.cell

Again, any main effects ( here Cu. level) that are included in interacting effects will be looked at through pairwise comparisons of the interacting factors

```{r phia_interaction means_FeDFB.cell, eval=TRUE}

(FeDFB.cell.means <- interactionMeans(lm_FeDFB.cell))
plot(FeDFB.cell.means)
```

This plot shows us the main effects (here none) and first order interactions (e.g. Fe level : Cu level). As per the "marginality principle" (see J. A. Nelder, "A reformulation of linear models," Journal of the Royal Statistical Society. Series A (General), vol. 140, no. 1, pp. 48{77, 1977.), those factors that are involved in interactions, should not be interpreted as single effects.

Integrated over high copper, Fe DFB uptake per cell is significantly higher in TO1005 than To 1003. The same is true for integrated low copper FeDFB uptake per cell. However, comparing low copper to high copper treatments, in TO 1005, FeDFB uptake decreases where FeDFB uptake increases in TO 1003.

#### Pairwise Comparisons

[Back Up](#BackUP)

In order to put actual numbers for the significant differences, I will do pairwise comparisons



*First:  Fe and Cu level*
```{r phia_interaction_Contrasts_Culevel_Felevel_FeDFB.cell, eval=TRUE}
testInteractions(lm_FeDFB.cell, fixed="Cu.level", across="Fe.level")
```

This means that there is no statistical difference in the FeDFB uptake per cell when we compare the control vs low Fe treatment (integrating over both strains). 

However,  there is significant higher FeDFB uptake per cell in lowFeCu treatment compared to low Cu. This is true in both strains. (F(1,14) = 43.48, p-val <0.000001).


```{r phia_interaction_Contrasts_Felevel_and_Cu.level_FeDFB.cell, eval=TRUE}
testInteractions(lm_FeDFB.cell, fixed = "Fe.level", across="Cu.level")
```

This means that there is slightly significant decrease in FeDFB uptake per cell from control to low Cu treatment in both strains (F(1,14) = 9.45, p-val = 0.02).  

When adding the Cu-co-limitation (i.e. comparing FeCu-colimitation) to Fe limitation, Fe DFB uptake is slightly significantly increased in both strains (F(1,14) = 6.48, p-val = 0.02) (Again, integrated for both strains)

*Second:  Species and Fe. level*
```{r phia_interaction_Contrasts_Species_Felevel_FeDFB.cell, eval=TRUE}
testInteractions(lm_FeDFB.cell, fixed="Species", across="Fe.level")
```

Comparing high Fe to low iron shows a statistical increase in Fe DFB uptake per cell in TO 1005 only (F(1,14) = 29.94, p=val < 0.001). Even though TO 1003 is trending to increase FeDFB uptake as well, this is not statistically significant (F (1,4) = 3.60, p-val = 0.08)

```{r phia_interaction_Contrasts_Felevel_and_Species_FeDFB.cell, eval=TRUE}
testInteractions(lm_FeDFB.cell, fixed = "Fe.level", across="Species")
```

Under high Fe condition, both strains have similar Fe DFB uptake per cell. However, under low Fe condition, they have significantly different Fe DFB uptake. Namely, TO 1005 has increase FeDFB uptake both under low Fe and low FeCu condition (F (1,14) = 30.62, p-val < 0.001). 

*Third:  Species and Cu. level*
```{r phia_interaction_Contrasts_Species_Culevel_FeDFB.cell, eval=TRUE}
testInteractions(lm_FeDFB.cell, fixed="Species", across="Cu.level")
```

Comparing the combined high Cu (control and low Fe) to the combined low Cu treatments (low Cu and low FeCu), neither strain showsshows a significant difference in FeDFB uptake.

```{r phia_interaction_Contrasts_Culevel_and_Species_FeDFB.cell, eval=TRUE}
testInteractions(lm_FeDFB.cell, fixed = "Cu.level", across="Species")
```

Under high Cu conditions, the two strains have statistically very different FeDFB uptake rates (F(1,14) = 28.14, p-val = 0.0002).They are just somewhat differnet under low Cu treatments (F(1,14) = 3.18, p-val = 0.096)

###Summary Fe DFB uptake per Cell

__low Cu__ decreases FeDFB uptake per cell in both strains compared to the control treatment (F(1,14) = 9.45, p-val = 0.02.


However,  there is significant higher FeDFB uptake per cell in lowFeCu treatment compared to low Cu. This is true in both strains. (F(1,14) = 43.48, p-val <0.000001).

 

When adding the Cu-co-limitation (i.e. comparing FeCu-colimitation) to Fe limitation, Fe DFB uptake is slightly significantly increased in both strains (F(1,14) = 6.48, p-val = 0.02) (Again, integrated for both strains)

Comparing high Fe to low iron shows a statistical increase in Fe DFB uptake per cell in TO 1005 only (F(1,14) = 29.94, p=val < 0.001). Even though TO 1003 is trending to increase FeDFB uptake as well, this is not statistically significant (F (1,4) = 3.60, p-val = 0.08)

Under high Fe condition, both strains have similar Fe DFB uptake per cell. However, under low Fe condition, they have significantly different Fe DFB uptake. Namely, TO 1005 has increase FeDFB uptake both under low Fe and low FeCu condition (F (1,14) = 30.62, p-val < 0.001). 

Comparing the combined high Cu (control and low Fe) to the combined low Cu treatments (low Cu and low FeCu), neither strain showsshows a significant difference in FeDFB uptake.

Under high Cu conditions, the two strains have statistically very different FeDFB uptake rates (F(1,14) = 28.14, p-val = 0.0002).They are just somewhat differnet under low Cu treatments (F(1,14) = 3.18, p-val = 0.096)


<a id="FeDFB.cellvol"></a>

#### FeDFB per Cell Surface Area

[Back Up](#BackUP)

First a look at the graph: 

```{r graph_FeDFB.cellvol, eval=TRUE}
p <- ggplot (mydata , aes(Treatment, FeDFB.zmol.um.2.h.))
p + geom_point(aes(group=Merged, colour=Species), size = 3)+
  labs(title="Fe DFB uptake [zmol/um^2 * h]", x ="")+
  geom_point(data=mean.df , aes(Treatment, FeDFB.zmol.um.2.h., size=2, colour=Species), shape = 45, size = 9)+
  guides(alpha = "none", size = "none", shape = "none")+
  expand_limits(y=0)

```

OK, this looks really widely distributed!
Now we start with a linear model testing for all main effects and interactions possible:

```{r lm_all_FeDFB.cellvol, eval=TRUE}
lm_all_FeDFB.cellvol <- lm(data = mydata, FeDFB.zmol.um.2.h. ~ (Species * Fe.level * Cu.level))
summary(lm_all_FeDFB.cellvol) # we need to look at the actual anova to know where we need to look further
anova(lm_all_FeDFB.cellvol) 
```

There seems to be no *Species : Cu.level* interaction. Hence, we will take this interaction out in the next linear model:

```{r lm_FeDFB.cellvol, eval=TRUE}
lm_FeDFB.cellvol <- lm (data = mydata, FeDFB.zmol.um.2.h. ~ (Species + Fe.level + Cu.level)^2 - Species:Cu.level)

summary(lm_FeDFB.cellvol) # we need to look at the actual anova to knwo where we need to look further
plot.new()
plot(lm_FeDFB.cellvol)

anova(lm_FeDFB.cellvol)
```

### Anova Table - FeDFB.cell Surface

Looking at the ANOVA table for the linear model that _does not_ test for interactions between Species : Cu.level for the data __FeDFB.cell surface__, we see the following significant factors:


* __Species__ alone has a significant effect 
* __Fe. level__ alone has a significant effect  
* __Cu level__ alone has no significant effect 
* there is  an __interaction__ between __Fe level and Cu level__ (F (1, 16) = 11.24, p-val = 0.004)
* there is  an __interaction__ between __Species and Fe level__ (F (1, 16) = 7.50, p-val = 0.014)



### Using the `phia` package to look into significant effects regarding FeDFB.cellvol

Again, any main effects ( here Cu. level) that are included in interacting effects will be looked at through pairwise comparisons of the interacting factors

```{r phia_interaction means_FeDFB.cellvol, eval=TRUE}

(FeDFB.cellvol.means <- interactionMeans(lm_FeDFB.cellvol))
plot(FeDFB.cellvol.means)
```

This plot shows us the main effects (here Species in relation to Cu level) and first order interactions (here Fe level : Cu level, and species: Fe level). As per the "marginality principle" (see J. A. Nelder, "A reformulation of linear models," Journal of the Royal Statistical Society. Series A (General), vol. 140, no. 1, pp. 48{77, 1977.), those factors that are involved in interactions, should not be interpreted as single effects.


#### Pairwise Comparisons

[Back Up](#BackUP)

In order to put actual numbers for the significant differences, I will do pairwise comparisons


```{r phia_interaction_Contrasts_Culevel_Felevel_FeDFB.cellvol, eval=TRUE}
testInteractions(lm_FeDFB.cellvol, fixed="Cu.level", across="Fe.level")
```

### From here I need to proceed!!!!!
This means that there is no statistical difference in the FeDFB uptake per cell surface when we compare the control vs low Fe treatment (integrating over both strains). 

However,  there is significant higher FeDFB uptake per cell in lowFeCu treatment compared to low Cu. This is true in both strains. (F(1,16) = 36.19, p-val <0.0001).


```{r phia_interaction_Contrasts_Felevel_and_Cu.level_FeDFB.cellvol, eval=TRUE}
testInteractions(lm_FeDFB.cellvol, fixed = "Fe.level", across="Cu.level")
```

This means that there is no significant change in FeDFB uptake per cell from control to low Cu treatment (integrated over both strains) (F(1,16) = 2.88, p-val = 0.11). 

However, when we compare low Fe to low FeCu treatment, there is a significant decrease in FeDFB uptake per cell surface integrated over both strains (F(1,16) = 9.27, p-val = 0.02). When we look at the graph, we see that this is mainly due to the large effect of lowFeCu in strain TO 1003!

*Second: Species and Fe.level*

```{r phia_interaction_Contrasts_Species_Felevel_FeDFB.cellvol, eval=TRUE}
testInteractions(lm_FeDFB.cellvol, fixed="Species", across="Fe.level")
```

TO 1003 has no statistical difference between the integrated high Fe vs integrated low Fe treatments. This is mainly due to the same FeDFB per cell surface rate in low Cu and low Fe. 

In TO 1005, integrated high Fe vs low Fe shows that ther is significantly higher FeDFB uptake per cell surface in lowFe treatments (F(1,16) = 28.32, p-val = 0.0001).


```{r phia_interaction_Contrasts_Felevel_and_Species_FeDFB.cellvol, eval=TRUE}
testInteractions(lm_FeDFB.cellvol, fixed = "Fe.level", across="Species")
```

This means that there is no significant difference between the two strains under high Fe in FeDFB uptake per cell surface (F(1,16, .344, p-val = 0.57). 

Under low Fe conditions there is a striking difference between TO 1005 and To 1003 (F(1,16) = 19.88, p-val < 0.001). When we look at the graph, we see that TO 1005 has almost the same high feDFB uptake per cell surface under low Fe as it has under low FeCu. TO 1003 has lower FeDFB uptake under low Fe than under its control treatment. But even under lowFeCu, it has still lower FeDFB uptake than TO 1005.

###Summary Fe DFB uptake per Cell











<a id="14C.alpha.cell"></a>

#### 14C Uptake per Cell - alpha

[Back Up](#BackUP)

First a look at the graph: 

```{r graph_14C.alpha.cell, eval=TRUE}
p <- ggplot (mydata , aes(Treatment, X14C.per.Cell.Vol.alpha))
p + geom_point(aes(group=Merged, colour=Species), size = 3, alpha=0.5)+
  labs(title="14C uptake per cell vol - alpha", x ="")+
  geom_point(data=mean.df , aes(Treatment, X14C.per.Cell.Vol.alpha, size=2, colour=Species), shape = 45, size = 9)+
  guides(alpha = "none", size = "none", shape = "none")+
  expand_limits(y=0)

```

I double checked the raw data: Yes, some points look almost the same, but they are not!

Now we start with a linear model testing for all main effects and interactions possible:

```{r lm_all_14C.alpha.cell, eval=TRUE}
lm_all_14C.alpha.cell <- lm(data = mydata, X14C.per.Cell.Vol.alpha ~ (Species * Fe.level * Cu.level))
summary(lm_all_14C.alpha.cell) # we need to look at the actual anova to know where we need to look further
anova(lm_all_14C.alpha.cell) 
```

There seems to be no *Fe.level : Cu.level* interaction. Hence, we will take this interaction out in the next linear model:
(Note: I leave it in)
```{r lm_14C.alpha.cell, eval=TRUE}
lm_14C.alpha.cell <- lm (data = mydata, X14C.per.Cell.Vol.alpha ~ (Species * Fe.level * Cu.level))

summary(lm_14C.alpha.cell) # we need to look at the actual anova to knwo where we need to look further
plot.new()
plot(lm_14C.alpha.cell)

anova(lm_14C.alpha.cell)
```

### Anova Table - 14C Uptake per Cell - alpha

Looking at the ANOVA table for the linear model that tests for all interactions for the data __14C.alpha.cell__, we see the following significant factors:


* __Species__ alone has no significant effect 
* __Fe. level__ alone has a slightly significant effect  (F (1, 16) = 4.65, p-val = 0.047)
* __Cu level__ alone has no significant effect 
* there is  an __trend towards an interaction__ between __Species and Fe level__ (F (1, 16) = 3.23, p-val = 0.09)
* there is  an __interaction__ between __Species and Cu level__ (F (1, 16) = 7.50, p-val = 0.014)



### Using the `phia` package to look into significant effects regarding 14C.alpha.cell

Again, any main effects ( here Cu. level) that are included in interacting effects will be looked at through pairwise comparisons of the interacting factors

```{r phia_interaction means_14C.alpha.cell, eval=TRUE}

(C14.alpha.cell.means <- interactionMeans(lm_14C.alpha.cell))
plot(C14.alpha.cell.means)
```

This plot shows us the main effects (here Fe level) and first order interactions (here Species : Cu level). As per the "marginality principle" (see J. A. Nelder, "A reformulation of linear models," Journal of the Royal Statistical Society. Series A (General), vol. 140, no. 1, pp. 48{77, 1977.), those factors that are involved in interactions, should not be interpreted as single effects.


#### Pairwise Comparisons

[Back Up](#BackUP)

In order to put actual numbers for the significant differences, I will do pairwise comparisons

*First: Species and Cu. level*
```{r phia_interaction_Contrasts_Species_Culevel_14C.alpha.cell, eval=TRUE}
testInteractions(lm_14C.alpha.cell, fixed="Species", across="Cu.level")
```

_alpha_ in the PE curve of 14C uptake per cell vol _decreases_ significantly in _TO 1003_ in response to _low Cu_  (F(1,16) = 8.78, p-val = 0.02). The same can not be said for TO 1005. This is probably mainly due to the increase in alpha in repsonse to low Cu and the decrease in alpha in responde to lowFeCu treatment in this strain.


```{r phia_interaction_Contrasts_Culevel_and_Species_14C.alpha.cell, eval=TRUE}
testInteractions(lm_14C.alpha.cell, fixed = "Cu.level", across="Species")
```

Integrated over the high Cu treatment, the two species have somehwat similat alpha values (F(1,16) = 3.16, p-val = 0.09). 

HOwever, integrating over the low Cu treatments, the two species do have significantly different responses in their alpha value (F(1,16) = 7.81, p-val = 0.03). When we look at the graph, we see that this is mainly due to the large difference int he low Cu treatment between the strains.

*Second: Species and Fe.level*

```{r phia_interaction_Contrasts_Species_Felevel_14C.alpha.cell, eval=TRUE}
testInteractions(lm_14C.alpha.cell, fixed="Species", across="Fe.level")
```

Here it is the other way around: _TO 1003_ has no significant differences in its alpha response (of the PE curve 14c uptake per cell vol) when integrating its high Fe vs low Fe treatments (F(1,16) = 0.07), p-val = 0.80). 

_TO 1005_ on the other hand does show a decrease in its initial slope alpha of its PE curve (F(1,16) = 7.81, p-val = 0.03)


```{r phia_interaction_Contrasts_Felevel_and_Species_14C.alpha.cell, eval=TRUE}
testInteractions(lm_14C.alpha.cell, fixed = "Fe.level", across="Species")
```

When we compare either the integrated high Fe or the integrated low Fe values of alpha of the two strains, no significant difference betweent he two strains can be seen.

###Summary 14C per cell vol - alpha






<a id="14C.alpha.chla"></a>

#### 14C Uptake per Chl a - alpha


[Back Up](#BackUP)

First a look at the graph: 

```{r graph_14C.alpha.chla, eval=TRUE}
p <- ggplot (mydata , aes(Treatment, X14C.per.Chla.alpha))
p + geom_point(aes(group=Merged, colour=Species), size = 3, alpha=0.5)+
  labs(title="14C uptake per Chla - alpha", x ="")+
  geom_point(data=mean.df , aes(Treatment, X14C.per.Chla.alpha, size=2, colour=Species), shape = 45, size = 9)+
  guides(alpha = "none", size = "none", shape = "none")+
  expand_limits(y=0)

```

Now we start with a linear model testing for all main effects and interactions possible:

```{r lm_all_14C.alpha.chla, eval=TRUE}
lm_all_14C.alpha.chla <- lm(data = mydata, X14C.per.Chla.alpha ~ (Species * Fe.level * Cu.level))
summary(lm_all_14C.alpha.chla) # we need to look at the actual anova to know where we need to look further
anova(lm_all_14C.alpha.chla) 
```

There seems to be no *SPecies: Fe.level* interaction and no *Fe.level : Cu.level* interaction. However, there might be a three way Species:Fe.level:Cu.level* interaction. Let's leave everything in, again:


```{r lm_14C.alpha.chla, eval=TRUE}
lm_14C.alpha.chla <- lm (data = mydata, X14C.per.Chla.alpha ~ (Species * Fe.level * Cu.level))
summary(lm_14C.alpha.chla) # we need to look at the actual anova to knwo where we need to look further
plot.new()
plot(lm_14C.alpha.chla)

anova(lm_14C.alpha.chla)
```

### Anova Table - 14C Uptake per Chl a - alpha

Looking at the ANOVA table for the linear model that tests for all interactions for the data __14C.alpha.chla__, we see the following significant factors:


* __Species__ alone has a significant effect 
* __Fe. level__ alone has no significant effect  
* __Cu level__ alone has somewhat of an effect 
* there is  an __interaction__ between __Species and Cu level__ (F (1, 16) = 9.01, p-val = 0.009)
* there is  __somewhat of a three-way interaction__ between __Species, Fe level and Cu level__ (F (1, 16) = 3.15, p-val = 0.095)



### Using the `phia` package to look into significant effects regarding 14C.alpha.chla

Again, any main effects ( none here) that are included in interacting effects will be looked at through pairwise comparisons of the interacting factors

```{r phia_interaction means_14C.alpha.chla, eval=TRUE}

(C14.alpha.cell.means <- interactionMeans(lm_14C.alpha.chla))
plot(C14.alpha.cell.means)
```

This plot shows us the main effects (noen here) and first order interactions (here Species : Cu level). As per the "marginality principle" (see J. A. Nelder, "A reformulation of linear models," Journal of the Royal Statistical Society. Series A (General), vol. 140, no. 1, pp. 48{77, 1977.), those factors that are involved in interactions, should not be interpreted as single effects.


#### Pairwise Comparisons

[Back Up](#BackUP)

In order to put actual numbers for the significant differences, I will do pairwise comparisons. As there is a hint of a three way interaction, I will fix one and run it across the two others and will go through all of them.

*First: Testing the three differnet variables against each other:*
```{r phia_interaction_Contrasts_Species_Culevel_and_Felevel_14C.alpha.chla, eval=TRUE}
testInteractions(lm_14C.alpha.chla, fixed="Species", across=c("Fe.level", "Cu.level")) # no significance
testInteractions(lm_14C.alpha.chla, fixed="Cu.level", across=c("Species", "Fe.level")) # no significance
testInteractions(lm_14C.alpha.chla, fixed="Fe.level", across=c("Species", "Cu.level"))
```

This last one suggests that only under high iron, we will find a difference between strains in response to Cu concentrations. Lets look at it:

*Second: Species : Cu level*
```{r phia_interaction_Contrasts_Species_Culevel_14C.alpha.chla, eval=TRUE}
testInteractions(lm_14C.alpha.chla, fixed="Species", across="Cu.level") # no significance
```

When looking at the _alpha_ values in the PE curve of 14C uptake normalized to Chla, __only TO 1003 _decreases_ its alpha__ in response to __low Cu__ significantly (F(1,16) = 11.98, p-val = 0.006). The same can not be said for TO 1005.


```{r phia_interaction_Contrasts_Culevel_and_Species_14C.alpha.chla, eval=TRUE}
testInteractions(lm_14C.alpha.chla, fixed = "Cu.level", across="Species")
```

Integrated over the high Cu treatment, the two species have extreley similar alpha values (F(1,16) = 0.012, p-val = 0.91). 

However, integrating over the low Cu treatments, the two species do have significantly different responses in their alpha value (F(1,16) = 18.96, p-val < 0.001). 



###Summary 14C per cell vol - alpha







<a id="14C.ek.chla"></a>

#### 14C Uptake per Chl a - ek



[Back Up](#BackUP)

First a look at the graph: 

```{r graph_14C.ek.chla, eval=TRUE}
p <- ggplot (mydata , aes(Treatment, X14C.per.Chla.ek))
p + geom_point(aes(group=Merged, colour=Species), size = 3, alpha=0.5)+
  labs(title="14C uptake per Chla - ek", x ="")+
  geom_point(data=mean.df , aes(Treatment, X14C.per.Chla.ek, size=2, colour=Species), shape = 45, size = 9)+
  guides(alpha = "none", size = "none", shape = "none")+
  expand_limits(y=0)

```

Now we start with a linear model testing for all main effects and interactions possible:

```{r lm_all_14C.ek.chla, eval=TRUE}
lm_all_14C.ek.chla <- lm(data = mydata, X14C.per.Chla.ek ~ (Species * Fe.level * Cu.level))
summary(lm_all_14C.ek.chla) # we need to look at the actual anova to know where we need to look further
anova(lm_all_14C.ek.chla) 
```

There seems to be a strong three way *Species:Fe.level:Cu.level* interaction. Let's leave everything in, again:


```{r lm_14C.ek.chla, eval=TRUE}
lm_14C.ek.chla <- lm (data = mydata, X14C.per.Chla.ek ~ (Species * Fe.level * Cu.level))
summary(lm_14C.ek.chla) # we need to look at the actual anova to knwo where we need to look further
plot.new()
plot(lm_14C.ek.chla)

anova(lm_14C.ek.chla)
```

### Anova Table - 14C Uptake per Chl a - alpha

Looking at the ANOVA table for the linear model that tests for all interactions for the data __14C.ek.chla__, we see the following significant factors:


* __Species__ alone has a significant effect 
* __Fe. level__ alone has a significant effect  
* __Cu level__ alone has a significant effect 
* there is  an __interaction__ between __Fe level and Cu level__ 
* there is  __a strong three-way interaction__ between __Species, Fe level and Cu level__ (F (1, 16) = 20.67, p-val = 0.0003)



### Using the `phia` package to look into significant effects regarding 14C.ek.chla

Again, any main effects that are included in interacting effects will be looked at through pairwise comparisons of the interacting factors

```{r phia_interaction means_14C.ek.chla, eval=TRUE}

(C14.alpha.cell.means <- interactionMeans(lm_14C.ek.chla))
plot(C14.alpha.cell.means)
```

This plot shows us the main effects (none here) and first order interactions (here Species : Cu level). As per the "marginality principle" (see J. A. Nelder, "A reformulation of linear models," Journal of the Royal Statistical Society. Series A (General), vol. 140, no. 1, pp. 48{77, 1977.), those factors that are involved in interactions, should not be interpreted as single effects.


#### Pairwise Comparisons

[Back Up](#BackUP)

In order to put actual numbers for the significant differences, I will do pairwise comparisons. As there is a hint of a three way interaction, I will fix one and run it across the two others and will go through all of them.

*First: Testing the three differnet variables against each other:*
```{r phia_interaction_Contrasts_Species_Culevel_and_Felevel_14C.ek.chla, eval=TRUE}
testInteractions(lm_14C.ek.chla, fixed="Species", across=c("Fe.level", "Cu.level")) 
```

TO 1003 has an interaction effect between Fe.level and Cu.level (F(1,16) = 23.06, p-val = 0.0004), whereas TO 1005 does NOT have such an interaction effect.

```{r phia_interaction_Contrasts_Culevel_and_Species_Felevel_14C.ek.chla, eval=TRUE}
testInteractions(lm_14C.ek.chla, fixed="Cu.level", across=c("Species", "Fe.level")) # both significance
testInteractions(lm_14C.ek.chla, fixed="Fe.level", across=c("Species", "Cu.level")) # both significance
```



*Second: Species : Cu level*
```{r phia_interaction_Contrasts_Species_Culevel_14C.ek.chla, eval=TRUE}
testInteractions(lm_14C.ek.chla, fixed="Species", across="Cu.level") # no significance
```

When looking at the _ek_ values in the PE curve of 14C uptake normalized to Chla, __only TO 1005 _decreases_ its ek__ in response to __low Cu__ significantly (F(1,16) = 13.96, p-val = 0.004). The same can not be said for TO 1005.


```{r phia_interaction_Contrasts_Culevel_and_Species_14C.ek.chla, eval=TRUE}
testInteractions(lm_14C.ek.chla, fixed = "Cu.level", across="Species")
```

Integrated over the high Cu treatment, the two species do have somewhat significantly different responses in their ek value (F(1,16) = 6.64, p-val = 0.04).  

However, integrating over the low Cu treatments, the two species have fairly similar ek values (F(1,16) = 0.27, p-val = 0.61).

*Third: Species : Fe level*
```{r phia_interaction_Contrasts_Species_Felevel_14C.ek.chla, eval=TRUE}
testInteractions(lm_14C.ek.chla, fixed="Species", across="Fe.level") # no significance
```

When looking at the _ek_ values in the PE curve of 14C uptake normalized to Chla, __both strains _decrease_ their ek__ in response to __low Fe__ significantly (TO 1003: F(1,16) = 6.00, p-val = 0.03; TO 1005:F(1,16) = 10.58, p-val = 0.01 ). 


```{r phia_interaction_Contrasts_Felevel_and_Species_14C.ek.chla, eval=TRUE}
testInteractions(lm_14C.ek.chla, fixed = "Fe.level", across="Species")
```

Integrated over the high Fe treatment or over the low Fe treatment, the two species do have somewhat similar responses in their ek value.  

###Summary 14C per cell vol - alpha







<a id="AOX"></a>

#### AOX - Alternative Oxidase

[Back Up](#BackUP)

First a look at the graph: 

```{r graph_AOX, eval=TRUE}
p <- ggplot (mydata , aes(Treatment, AOXactivity))
p + geom_point(aes(group=Merged, colour=Species), size = 3, alpha=0.5)+
  labs(title="AOX activity (%)", x ="")+
  geom_point(data=mean.df , aes(Treatment, AOXactivity, size=2, colour=Species), shape = 45, size = 9)+
  guides(alpha = "none", size = "none", shape = "none")+
  expand_limits(y=0)

```

Now we start with a linear model testing for all main effects and interactions possible:

```{r lm_all_AOX, eval=TRUE}
lm_all_AOX <- lm(data = mydata, AOXactivity ~ (Species * Fe.level * Cu.level))
summary(lm_all_AOX) # we need to look at the actual anova to know where we need to look further
anova(lm_all_AOX) 
```

Having both species combined, there doesn't seem to be a relationship between Fe/Cu level and the precentage of the involvement of Alternative Oxidase in TO 1003 and TO 1005 combined.

Just by looking at the graph however, it looks as if there might be relationship when we look at control vs the low Fe treatment at least in TO 1003. To look into this, I would like to look at the respective strain data only:

*First TO 1003:*
```{r TO1003lm_AOX, eval=TRUE}
TO1003 <-  mydata %>% filter (Species == "TO 1003") #subsetting data into TO 1003 only

lm_TO03_AOX <- lm (data = TO1003, AOXactivity ~ (Fe.level * Cu.level))
summary(lm_TO03_AOX) # we need to look at the actual anova to knwo where we need to look further
plot.new()
plot(lm_TO03_AOX)

anova(lm_TO03_AOX)
```

Indeed, for TO 1003, there seems to be an Fe effect (F (1,7) = 7.45), p=-val = 0.03)

*First TO 1005:*
```{r TO1005lm_AOX, eval=TRUE}
TO1005 <-  mydata %>% filter (Species == "TO 1005") #subsetting data into TO 1005 only

lm_TO05_AOX <- lm (data = TO1005, AOXactivity ~ (Fe.level * Cu.level))
summary(lm_TO05_AOX) # we need to look at the actual anova to knwo where we need to look further
plot.new()
plot(lm_TO05_AOX)

anova(lm_TO05_AOX)
```

Whereas, for TO 1005, there seems to be no Fe or Cu effect at all.

### Anova Table - 14C Uptake per Chl a - alpha

Looking at the ANOVA table for the linear model that tests for all interactions for the data __AOX__, we see the following significant factors:


* __Species__ alone has a significant effect 
* __Fe. level__ alone has a significant effect  
* __Cu level__ alone has a significant effect 
* there is  an __interaction__ between __Fe level and Cu level__ 
* there is  __a strong three-way interaction__ between __Species, Fe level and Cu level__ (F (1, 16) = 20.67, p-val = 0.0003)



### Using the `phia` package to look into significant effects regarding AOX

Again, any main effects that are included in interacting effects will be looked at through pairwise comparisons of the interacting factors

```{r phia_interaction means_TO03_AOX, eval=TRUE}

(TO03_AOX.means <- interactionMeans(lm_TO03_AOX))
plot(TO03_AOX.means)
```

This plot shows us the main effects (none here) and first order interactions (here Species : Cu level). As per the "marginality principle" (see J. A. Nelder, "A reformulation of linear models," Journal of the Royal Statistical Society. Series A (General), vol. 140, no. 1, pp. 48{77, 1977.), those factors that are involved in interactions, should not be interpreted as single effects.


#### Pairwise Comparisons

[Back Up](#BackUP)

In order to put actual numbers for the significant differences, I will do pairwise comparisons. As there is a hint of a three way interaction, I will fix one and run it across the two others and will go through all of them.

*TO 1003 Fe vs Cu level:*
```{r phia_interaction_Contrasts_TO03_Felevel_and_Culevel_AOX, eval=TRUE}
testInteractions(lm_TO03_AOX, fixed="Fe.level", across="Cu.level") 
```

Changing the Cu level does not have an effect on AOX activity in TO 1003

```{r phia_interaction_Contrasts_TO03_Culevel_and_Felevel_AOX, eval=TRUE}
testInteractions(lm_TO03_AOX, fixed="Cu.level", across="Fe.level") 
```

Lowering the Fe level under high Cu conditions has the tendency to increase AOX activity (F(1,7) = 6.25, p-val = 0.08).
There is no such tendency under low Cu conditions. 


###Summary 14C per cell vol - alpha






<a id="O2.Chla"></a>

#### Gross Productivity per Chla (mol O2 * mol Chl a^-1 * h^-1)

[Back Up](#BackUP)

First a look at the graph: 

```{r graph_O2.Chla, eval=TRUE}
p <- ggplot (mydata , aes(Treatment, GrossPchla.mol.O2.mol.Chla..h.))
p + geom_point(aes(group=Merged, colour=Species), size = 3, alpha=0.5)+
  labs(title="Gross Production O2 per Chl a", x ="")+
  geom_point(data=mean.df , aes(Treatment, GrossPchla.mol.O2.mol.Chla..h., size=2, colour=Species), shape = 45, size = 9)+
  guides(alpha = "none", size = "none", shape = "none")+
  expand_limits(y=0)

```

Now we start with a linear model testing for all main effects and interactions possible:

```{r lm_all_O2.Chla, eval=TRUE}
lm_all_O2.Chla <- lm(data = mydata, GrossPchla.mol.O2.mol.Chla..h. ~ (Species * Fe.level * Cu.level))
summary(lm_all_O2.Chla) # we need to look at the actual anova to know where we need to look further
anova(lm_all_O2.Chla) 
```

As there seems to be a hint of three way *Species:Fe.level:Cu.level* interaction. Let's leave everything in:


```{r plot lm_all_O2.Chla, eval=TRUE}
plot.new()
plot(lm_all_O2.Chla)

anova(lm_all_O2.Chla)
```

### Anova Table - 14C Uptake per Chl a - alpha

Looking at the ANOVA table for the linear model that tests for all interactions for the data __O2.Chla__, we see the following significant factors:


* __Species__ alone has no significant effect 
* __Fe. level__ alone has no significant effect  
* __Cu level__ alone has a significant effect 
* there is  an __interaction__ between __Species and Cu level__ (F(1,14) = 14.96, p-val = 0.002)
* there is  an __interaction__ between __Fe level and Cu level__ (F(1,14) = 6.42, p-val = 0.02)
* there is  __a tendency for a three-way interaction__ between __Species, Fe level and Cu level__ (F (1, 14) = 4.08, p-val = 0.06)



### Using the `phia` package to look into significant effects regarding O2.Chla

Again, any main effects that are included in interacting effects will be looked at through pairwise comparisons of the interacting factors

```{r phia_interaction means_O2.Chla, eval=TRUE}

(O2.Chla.means <- interactionMeans(lm_all_O2.Chla))
plot(O2.Chla.means)
```

This plot shows us the main effects (none here) and first order interactions (here Species : Cu level). As per the "marginality principle" (see J. A. Nelder, "A reformulation of linear models," Journal of the Royal Statistical Society. Series A (General), vol. 140, no. 1, pp. 48{77, 1977.), those factors that are involved in interactions, should not be interpreted as single effects.


#### Pairwise Comparisons

[Back Up](#BackUP)

In order to put actual numbers for the significant differences, I will do pairwise comparisons. As there is a hint of a three way interaction, I will fix one and run it across the two others and will go through all of them.

*First: Testing the three differnet variables against each other:*
```{r phia_interaction_Contrasts_Species_Culevel_and_Felevel_O2.Chla, eval=TRUE}
testInteractions(lm_all_O2.Chla, fixed="Species", across=c("Fe.level", "Cu.level")) 
```

TO 1003 has an interaction effect between Fe.level and Cu.level (F(1,14) = 17.34, p-val = 0.002), whereas TO 1005 does NOT have such an interaction effect.

```{r phia_interaction_Contrasts_Species_and_Culevel_against_Felevel_O2.Chla, eval=TRUE}
testInteractions(lm_all_O2.Chla, fixed=c("Species","Cu.level"), across="Fe.level") 
```
This shows that the interaction effect is due to the fact that lowering Fe levels is only significant under high Cu conditions but not under low Cu conditions. And this is only true for TO 1003 and not To 1005.

Low Fe compared to control lowers Gross P (O2 per Chla) in TO 1003 (F(1,14) = 12.51, p-val = 0.01)

```{r phia_interaction_Contrasts_Species_and_Felevel_against_Culevel_O2.Chla, eval=TRUE}
testInteractions(lm_all_O2.Chla, fixed=c("Species","Fe.level"), across="Cu.level") 
```
The same is true for Cu: lowering Cu levels is only significant under high Fe conditions and only for TO 1003 and not for TO 1005 or under low Fe conditions.

Low Cu compared to control lowers Gross P (O2 per Chla) in TO 1003 (F(1,14) = 30.81, p-val = 0.0003)

```{r phia_interaction_Contrasts_Felevel_and_Culevel_against_Species_O2.Chla, eval=TRUE}
testInteractions(lm_all_O2.Chla, fixed=c("Cu.level","Fe.level"), across="Species") 
```
The Gross productivity (O2 per Chla) only seems to be somewhat significantly different in the low Cu treatment (F(1,14) = 8.01, p-val = 0.05)

```{r phia_interaction_Contrasts_Culevel_and_Species_Felevel_O2.Chla, eval=TRUE}
testInteractions(lm_all_O2.Chla, fixed="Cu.level", across=c("Species", "Fe.level")) # no significance
testInteractions(lm_all_O2.Chla, fixed="Fe.level", across=c("Species", "Cu.level")) # 
```

Under high Fe. species and Cu level do have an interaction effect (F(1,14) = 10.47, p-val = 0.01)

*Second: Species : Cu level*
```{r phia_interaction_Contrasts_Species_Culevel_O2.Chla, eval=TRUE}
testInteractions(lm_all_O2.Chla, fixed="Species", across="Cu.level") # no significance
```

__Low Cu decreases Gross P__ (O2 per Chl a) significantly in __TO 1003__ (F(1,14) = 10.48, p-val = 0.01) but __not in TO 1005__


```{r phia_interaction_Contrasts_Culevel_and_Species_O2.Chla, eval=TRUE}
testInteractions(lm_all_O2.Chla, fixed = "Cu.level", across="Species")
```

Under the integrated low Cu treatments, TO 1003 has significantly lower Gross P rates (O2 per Chl a) thatn To 1005 (F(1,14) = 8.82, p-val = 0.02)

Under the integrated high Cu treatments, the rates of the two strains is not significantly different.

*Third: Fe and Cu level*
```{r phia_interaction_Contrasts__Felevel_Culevel_O2.Chla, eval=TRUE}
testInteractions(lm_all_O2.Chla, fixed="Fe.level", across="Cu.level") # no significance
```

Low Cu compared to control decreases Gross P (O2 per Chla) significantly in the integrates strain data. Looking at the data this is probably mainly due to the decrease in TO 1003 (F(1,14) = 21.3, p-val = 0.0008).

This effect can not be seen in low FeCu compared to low Fe.


```{r phia_interaction_Contrasts_Culevel_and_Felevel_O2.Chla, eval=TRUE}
testInteractions(lm_all_O2.Chla, fixed = "Cu.level", across="Fe.level")
```

Additionally, low Fe compared to control decreases Gross P (O2 per Chla) also significantly in the integrated strain data (F(1,14) = 10.33, p-val = 0.01). When comparing low Fecu to lowFe treatments, Gross P slightly increases (F(1,14) = 4.88, p-val = 0.04)


###Summary 14C per cell vol - alpha








<a id="O2.Cell"></a>

#### Gross Productivity per Cell (mol O2 * cell ^-1 * h^-1)

[Back Up](#BackUP)

First a look at the graph: 

```{r graph_O2.Cell, eval=TRUE}
mydata <- mydata %>% mutate(nmol_O2_per_cell = GrossPcell..mol.O2.cell..h. * 10^9)
mean.df <- mean.df %>% mutate(nmol_O2_per_cell = GrossPcell.mol.O2.cell..h. * 10^9)

p <- ggplot (mydata , aes(Treatment, nmol_O2_per_cell))
p + geom_point(aes(group=Merged, colour=Species), size = 3)+
  labs(title="Gross Productivity (nmol O2 per cell * h)", x ="")+
  geom_point(data=mean.df , aes(Treatment, nmol_O2_per_cell, size=2, colour=Species), shape = 45, size = 9)+
  guides(alpha = "none", size = "none", shape = "none")+
  expand_limits(y=0)

```

Now we start with a linear model testing for all main effects and interactions possible:

```{r lm_all_O2.Cell, eval=TRUE}
lm_all_O2.Cell <- lm(data = mydata, nmol_O2_per_cell ~ (Species * Fe.level * Cu.level))
summary(lm_all_O2.Cell) # we need to look at the actual anova to know where we need to look further
anova(lm_all_O2.Cell) 
```

There seems to be no *Species: Fe.level* interaction so let's take this interaction out


```{r lm_O2.Cell, eval=TRUE}
lm_O2.Cell <- lm (data = mydata, nmol_O2_per_cell ~ (Species +  Fe.level + Cu.level)^2 - Species : Fe.level)
summary(lm_O2.Cell) # we need to look at the actual anova to knwo where we need to look further
plot.new()
plot(lm_O2.Cell)

anova(lm_O2.Cell)
```

### Anova Table - 14C Uptake per Chl a - alpha

Looking at the ANOVA table for the linear model that tests for all interactions for the data __O2.Cell__, we see the following significant factors:


* __Species__ alone has no significant effect 
* __Fe. level__ alone has a significant effect  
* __Cu level__ alone has a significant effect 
* there is  an __interaction__ between __Species and Cu level__ (F (1, 16) = 6.49, p-val = 0.02)
* there is  an __interaction__ between __Fe level and Cu level__ (F (1, 16) = 15.99, p-val = 0.001)



### Using the `phia` package to look into significant effects regarding O2.Cell

Again, any main effects ( none here) that are included in interacting effects will be looked at through pairwise comparisons of the interacting factors

```{r phia_interaction means_O2.Cell, eval=TRUE}

(O2.Cell.means <- interactionMeans(lm_O2.Cell))
plot(O2.Cell.means)
```

This plot shows us the main effects (noen here) and first order interactions (here Species : Cu level). As per the "marginality principle" (see J. A. Nelder, "A reformulation of linear models," Journal of the Royal Statistical Society. Series A (General), vol. 140, no. 1, pp. 48{77, 1977.), those factors that are involved in interactions, should not be interpreted as single effects.


#### Pairwise Comparisons

[Back Up](#BackUP)

*First: Species : Cu level*
```{r phia_interaction_Contrasts_Species_Culevel_O2.Cell, eval=TRUE}
testInteractions(lm_O2.Cell, fixed="Species", across="Cu.level") 

```

In TO 1003, integrated low Cu treatments result in a significant decrease in O2 per cell production (F(1, 16) = 29.77, p-val = 0.0001). In TO 1005 there seems to be a similar trend (not statsistically significant, though) (F(1, 16) = 3.51, p-val = 0.079).


```{r phia_interaction_Contrasts_Culevel_and_Species_O2.Cell, eval=TRUE}
testInteractions(lm_O2.Cell, fixed = "Cu.level", across="Species")
```

If high Cu treatments are integrated and compared between strains, they show similar oxygen per cell production rates. The same can be said for integrated low Cu treatments.

*Second: Fe level : Cu level*
```{r phia_interaction_Contrasts_Felevel_Culevel_O2.Cell, eval=TRUE}
testInteractions(lm_O2.Cell, fixed="Fe.level", across="Cu.level") # no significance

```

Low Cu compared to control results in a significant reduction in O2 production per cell across both strains (F(1, 16) = 47.13, p-val < 0.00001).  

Comparing lowFeCu to low Fe does not reduce the rate across strains.

```{r phia_interaction_Contrasts_Culevel_and_Felevel_O2.Cell, eval=TRUE}
testInteractions(lm_O2.Cell, fixed = "Cu.level", across="Fe.level")
```
However, low Fe compared to control results also in a significant reduction in O2 production per cell across both strains (F(1, 16) = 28.73, p-val = 0.0001).


###Summary 14C per cell vol - alpha







<a id="O2.Cell.vol"></a>

#### Gross Productivity per Cell Volume (mol O2 * cell vol ^-1 * h^-1)

[Back Up](#BackUP)

First a look at the graph: 

```{r graph_O2.Cell.vol, eval=TRUE}
p <- ggplot (mydata , aes(Treatment, Gross.P.CellVol..mol.O2.L.))
p + geom_point(aes(group=Merged, colour=Species), size = 3)+
  labs(title="Gross Productivity (mol O2 per cell vol (L) * h)", x ="")+
  geom_point(data=mean.df , aes(Treatment, Gross.P.CellVol..mol.O2.L., size=2, colour=Species), shape = 45, size = 9)+
  guides(alpha = "none", size = "none", shape = "none")+
  expand_limits(y=0)

```

Now we start with a linear model testing for all main effects and interactions possible:

```{r lm_all_O2.Cell.vol, eval=TRUE}
lm_all_O2.Cell.vol <- lm(data = mydata, Gross.P.CellVol..mol.O2.L. ~ (Species * Fe.level * Cu.level))
summary(lm_all_O2.Cell.vol) # we need to look at the actual anova to know where we need to look further
anova(lm_all_O2.Cell.vol) 
```

There seems to be no *Species: Fe.level* interaction so let's take this interaction out


```{r lm_O2.Cell.vol, eval=TRUE}
lm_O2.Cell.vol <- lm (data = mydata, Gross.P.CellVol..mol.O2.L. ~ (Species +  Fe.level + Cu.level)^2 - Species : Fe.level)
summary(lm_O2.Cell.vol) # we need to look at the actual anova to knwo where we need to look further
plot.new()
plot(lm_O2.Cell.vol)

anova(lm_O2.Cell.vol)
```

### Anova Table - 14C Uptake per Chl a - alpha

Looking at the ANOVA table for the linear model that tests for all interactions for the data __O2.Cell.vol__, we see the following significant factors:


* __Species__ alone has no significant effect 
* __Fe. level__ alone has a significant effect  
* __Cu level__ alone has a significant effect 
* there is  an __interaction__ between __Species and Cu level__ (F (1, 16) = 7.08, p-val = 0.017)
* there is  an __interaction__ between __Fe level and Cu level__ (F (1, 16) = 5.61, p-val = 0.03)



### Using the `phia` package to look into significant effects regarding O2.Cell.vol

Again, any main effects ( none here) that are included in interacting effects will be looked at through pairwise comparisons of the interacting factors

```{r phia_interaction means_O2.Cell.vol, eval=TRUE}

(O2.Cell.vol.means <- interactionMeans(lm_O2.Cell.vol))
plot(O2.Cell.vol.means)
```

This plot shows us the main effects (none here) and first order interactions (here Species : Cu level). As per the "marginality principle" (see J. A. Nelder, "A reformulation of linear models," Journal of the Royal Statistical Society. Series A (General), vol. 140, no. 1, pp. 48{77, 1977.), those factors that are involved in interactions, should not be interpreted as single effects.


#### Pairwise Comparisons

[Back Up](#BackUP)

*First: Species : Cu level*
```{r phia_interaction_Contrasts_Species_Culevel_O2.Cell.vol, eval=TRUE}
testInteractions(lm_O2.Cell.vol, fixed="Species", across="Cu.level") 

```

In TO 1003, integrated low Cu treatments result in a significant decrease in O2 per cell vol production (F(1, 16) = 14.06, p-val = 0.004). In TO 1005 this seems to be absolutely not the case (F(1, 16) = 0, p-val = 0.995). WHen looking at the graph this makes sense as O2 production per cell vol is highest in the control (as expected) and it decrease in response to low Cu, it decreases even more in response to low Fe but then increases again in low FeCu (when compared to low Fe). This means, when we integrate the high Cu data (control and lowFe) and compare that to the integrated low Cu data (lowCu and low FeCu), there is practically no difference.

```{r phia_interaction_Contrasts_Culevel_and_Species_O2.Cell.vol, eval=TRUE}
testInteractions(lm_O2.Cell.vol, fixed = "Cu.level", across="Species")
```

If high Cu treatments are integrated and compared between strains, they show similar oxygen per cell vol production rates. The same can be said for integrated low Cu treatments.

*Second: Fe level : Cu level*
```{r phia_interaction_Contrasts_Felevel_Culevel_O2.Cell.vol, eval=TRUE}
testInteractions(lm_O2.Cell.vol, fixed="Fe.level", across="Cu.level") # no significance

```

Low Cu compared to control results in a significant reduction in O2 production per cell vol across both strains (F(1, 16) = 14.12, p-val < 0.003).  

Comparing lowFeCu to low Fe does not reduce the rate across strains.

```{r phia_interaction_Contrasts_Culevel_and_Felevel_O2.Cell.vol, eval=TRUE}
testInteractions(lm_O2.Cell.vol, fixed = "Cu.level", across="Fe.level")
```
However, low Fe compared to control results also in a significant reduction in O2 production per cell vol across both strains (F(1, 16) = 9.25, p-val = 0.016).


###Summary 14C per cell vol - alpha



### Making the big Statistical Summary Tables

####First for Growthrate.dd

```{r stat_SummaryTable_Growthrate.dd, eval = FALSE}

lm_Growthrate.dd <- lm(data=mydata, Growthrate.dd.1~(Species+Fe.level+Cu.level)^2-Species:Cu.level) 

#~~~~~~~~~~~~~~
anova_Growthrate.dd <- anova(lm_Growthrate.dd)
anova_Growthrate.dd <- anova_Growthrate.dd %>% 
  mutate(Analysis = "anova", Data = "Growthrate.dd", Effects_Tested = rownames(anova_Growthrate.dd))

anova_Growthrate.dd <- data.frame(anova_Growthrate.dd[, 6:8], anova_Growthrate.dd[,1:5])
#~~~~~~~~~~~~~~
phia_Growthrate.dd_Species_Cu_vs_Fe <- testInteractions(lm_Growthrate.dd, fixed=c("Species", "Cu.level"), across="Fe.level")
phia_Growthrate.dd_Species_Cu_vs_Fe <- phia_Growthrate.dd_Species_Cu_vs_Fe %>% 
  mutate(Analysis = "phia_interaction", Data = "Growthrate.dd",test_intrctn = "Species_Cu_vs_Fe", tested = rownames(phia_Growthrate.dd_Species_Cu_vs_Fe))

phia_Growthrate.dd_Species_Cu_vs_Fe <- data.frame(phia_Growthrate.dd_Species_Cu_vs_Fe[,6:9], phia_Growthrate.dd_Species_Cu_vs_Fe[, 1:5])
#~~~~~~~~~~~~~~

phia_Growthrate.dd_Species_Fe_vs_Cu <- testInteractions(lm_Growthrate.dd, fixed=c("Species", "Fe.level"), across="Cu.level")
phia_Growthrate.dd_Species_Fe_vs_Cu <- phia_Growthrate.dd_Species_Fe_vs_Cu %>% 
  mutate(Analysis = "phia_interaction", Data = "Growthrate.dd",test_intrctn = "Species_Fe_vs_Cu", tested = rownames(phia_Growthrate.dd_Species_Fe_vs_Cu))

phia_Growthrate.dd_Species_Fe_vs_Cu <- data.frame(phia_Growthrate.dd_Species_Fe_vs_Cu[,6:9], phia_Growthrate.dd_Species_Fe_vs_Cu[, 1:5])

#~~~~~~~~~~~~~~

phia_Growthrate.dd_Fe_Cu_vs_Species <- testInteractions(lm_Growthrate.dd, fixed=c("Fe.level", "Cu.level"), across="Species")
phia_Growthrate.dd_Fe_Cu_vs_Species <- phia_Growthrate.dd_Fe_Cu_vs_Species %>% 
  mutate(Analysis = "phia_interaction", Data = "Growthrate.dd",test_intrctn = "Fe_Cu_vs_Species", tested = rownames(phia_Growthrate.dd_Fe_Cu_vs_Species))

phia_Growthrate.dd_Fe_Cu_vs_Species <- data.frame(phia_Growthrate.dd_Fe_Cu_vs_Species[,6:9], phia_Growthrate.dd_Fe_Cu_vs_Species[, 1:5])

#~~~~~~~~~~~~~~
#Fe vs Cu
phia_Growthrate.dd_Fe_vs_Cu <- testInteractions(lm_Growthrate.dd, fixed="Fe.level", across="Cu.level")
phia_Growthrate.dd_Fe_vs_Cu <- phia_Growthrate.dd_Fe_vs_Cu %>% 
  mutate(Analysis = "phia_interaction", Data = "Growthrate.dd",test_intrctn = "Fe_vs_Cu", tested = rownames(phia_Growthrate.dd_Fe_vs_Cu))

phia_Growthrate.dd_Fe_vs_Cu <- data.frame(phia_Growthrate.dd_Fe_vs_Cu[,6:9], phia_Growthrate.dd_Fe_vs_Cu[, 1:5])
#~~~~~~~~~~~~~~
#Cu vs Fe
phia_Growthrate.dd_Cu_vs_Fe <- testInteractions(lm_Growthrate.dd, fixed="Cu.level", across="Fe.level")
phia_Growthrate.dd_Cu_vs_Fe <- phia_Growthrate.dd_Cu_vs_Fe %>% 
  mutate(Analysis = "phia_interaction", Data = "Growthrate.dd",test_intrctn = "Cu_vs_Fe", tested = rownames(phia_Growthrate.dd_Cu_vs_Fe))

phia_Growthrate.dd_Cu_vs_Fe <- data.frame(phia_Growthrate.dd_Cu_vs_Fe[,6:9], phia_Growthrate.dd_Cu_vs_Fe[, 1:5])

#~~~~~~~~~~~~~~
#Species vs Fe
phia_Growthrate.dd_Species_vs_Fe <- testInteractions(lm_Growthrate.dd, fixed="Species", across="Fe.level")
phia_Growthrate.dd_Species_vs_Fe <- phia_Growthrate.dd_Species_vs_Fe %>% 
  mutate(Analysis = "phia_interaction", Data = "Growthrate.dd",test_intrctn = "Species_vs_Fe", tested = rownames(phia_Growthrate.dd_Species_vs_Fe))

phia_Growthrate.dd_Species_vs_Fe <- data.frame(phia_Growthrate.dd_Species_vs_Fe[,6:9], phia_Growthrate.dd_Species_vs_Fe[, 1:5])

#~~~~~~~~~~~~~~
#Fe vs Species
phia_Growthrate.dd_Fe_vs_Species <- testInteractions(lm_Growthrate.dd, fixed="Fe.level", across="Species")
phia_Growthrate.dd_Fe_vs_Species <- phia_Growthrate.dd_Fe_vs_Species %>% 
  mutate(Analysis = "phia_interaction", Data = "Growthrate.dd",test_intrctn = "Fe_vs_Species", tested = rownames(phia_Growthrate.dd_Fe_vs_Species))

phia_Growthrate.dd_Fe_vs_Species <- data.frame(phia_Growthrate.dd_Fe_vs_Species[,6:9], phia_Growthrate.dd_Fe_vs_Species[, 1:5])

#~~~~~~~~~~~~~~
#Species vs Cu
phia_Growthrate.dd_Species_vs_Cu <- testInteractions(lm_Growthrate.dd, fixed="Species", across="Cu.level")
phia_Growthrate.dd_Species_vs_Cu <- phia_Growthrate.dd_Species_vs_Cu %>% 
  mutate(Analysis = "phia_interaction", Data = "Growthrate.dd",test_intrctn = "Species_vs_Cu", tested = rownames(phia_Growthrate.dd_Species_vs_Cu))

phia_Growthrate.dd_Species_vs_Cu <- data.frame(phia_Growthrate.dd_Species_vs_Cu[,6:9], phia_Growthrate.dd_Species_vs_Cu[, 1:5])

#~~~~~~~~~~~~~~
#Cu vs Species
phia_Growthrate.dd_Cu_vs_Species <- testInteractions(lm_Growthrate.dd, fixed="Cu.level", across="Species")
phia_Growthrate.dd_Cu_vs_Species <- phia_Growthrate.dd_Cu_vs_Species %>% 
  mutate(Analysis = "phia_interaction", Data = "Growthrate.dd",test_intrctn = "Cu_vs_Species", tested = rownames(phia_Growthrate.dd_Cu_vs_Species))

phia_Growthrate.dd_Cu_vs_Species <- data.frame(phia_Growthrate.dd_Cu_vs_Species[,6:9], phia_Growthrate.dd_Cu_vs_Species[, 1:5])

#~~~~~~~~~~~~~~~~~~~

#making the big Phia_Growthrate.dd table

all_phia_Growthrate.dd <- bind_rows(phia_Growthrate.dd_Cu_vs_Species, phia_Growthrate.dd_Species_vs_Cu, phia_Growthrate.dd_Fe_vs_Species, phia_Growthrate.dd_Species_vs_Fe, phia_Growthrate.dd_Cu_vs_Fe, phia_Growthrate.dd_Fe_vs_Cu, phia_Growthrate.dd_Fe_Cu_vs_Species, phia_Growthrate.dd_Species_Fe_vs_Cu, phia_Growthrate.dd_Species_Cu_vs_Fe)

```


#### Now for Growthrate.percent

```{r stat_SummaryTable_Growthrate.percent, eval = FALSE}

#~~~~~~~~~~~~~~
anova_growthrate.percent <- anova(lm_Growthrate.percent)
anova_growthrate.percent <- anova_growthrate.percent %>% 
  mutate(Analysis = "anova", Data = "Growthrate.percent", Effects_Tested = rownames(anova_growthrate.percent))

anova_growthrate.percent <- data.frame(anova_growthrate.percent[, 6:8], anova_growthrate.percent[,1:5])
#~~~~~~~~~~~~~~
phia_Growthrate.percent_Species_Cu_vs_Fe <- testInteractions(lm_Growthrate.percent, fixed=c("Species", "Cu.level"), across="Fe.level")
phia_Growthrate.percent_Species_Cu_vs_Fe <- phia_Growthrate.percent_Species_Cu_vs_Fe %>% 
  mutate(Analysis = "phia_interaction", Data = "Growthrate.percent",test_intrctn = "Species_Cu_vs_Fe", tested = rownames(phia_Growthrate.percent_Species_Cu_vs_Fe))

phia_Growthrate.percent_Species_Cu_vs_Fe <- data.frame(phia_Growthrate.percent_Species_Cu_vs_Fe[,6:9], phia_Growthrate.percent_Species_Cu_vs_Fe[, 1:5])
#~~~~~~~~~~~~~~

phia_Growthrate.percent_Species_Fe_vs_Cu <- testInteractions(lm_Growthrate.percent, fixed=c("Species", "Fe.level"), across="Cu.level")
phia_Growthrate.percent_Species_Fe_vs_Cu <- phia_Growthrate.percent_Species_Fe_vs_Cu %>% 
  mutate(Analysis = "phia_interaction", Data = "Growthrate.percent",test_intrctn = "Species_Fe_vs_Cu", tested = rownames(phia_Growthrate.percent_Species_Fe_vs_Cu))

phia_Growthrate.percent_Species_Fe_vs_Cu <- data.frame(phia_Growthrate.percent_Species_Fe_vs_Cu[,6:9], phia_Growthrate.percent_Species_Fe_vs_Cu[, 1:5])

#~~~~~~~~~~~~~~

phia_Growthrate.percent_Fe_Cu_vs_Species <- testInteractions(lm_Growthrate.percent, fixed=c("Fe.level", "Cu.level"), across="Species")
phia_Growthrate.percent_Fe_Cu_vs_Species <- phia_Growthrate.percent_Fe_Cu_vs_Species %>% 
  mutate(Analysis = "phia_interaction", Data = "Growthrate.percent",test_intrctn = "Fe_Cu_vs_Species", tested = rownames(phia_Growthrate.percent_Fe_Cu_vs_Species))

phia_Growthrate.percent_Fe_Cu_vs_Species <- data.frame(phia_Growthrate.percent_Fe_Cu_vs_Species[,6:9], phia_Growthrate.percent_Fe_Cu_vs_Species[, 1:5])

#~~~~~~~~~~~~~~
#Fe vs Cu
phia_Growthrate.percent_Fe_vs_Cu <- testInteractions(lm_Growthrate.percent, fixed="Fe.level", across="Cu.level")
phia_Growthrate.percent_Fe_vs_Cu <- phia_Growthrate.percent_Fe_vs_Cu %>% 
  mutate(Analysis = "phia_interaction", Data = "Growthrate.percent",test_intrctn = "Fe_vs_Cu", tested = rownames(phia_Growthrate.percent_Fe_vs_Cu))

phia_Growthrate.percent_Fe_vs_Cu <- data.frame(phia_Growthrate.percent_Fe_vs_Cu[,6:9], phia_Growthrate.percent_Fe_vs_Cu[, 1:5])
#~~~~~~~~~~~~~~
#Cu vs Fe
phia_Growthrate.percent_Cu_vs_Fe <- testInteractions(lm_Growthrate.percent, fixed="Cu.level", across="Fe.level")
phia_Growthrate.percent_Cu_vs_Fe <- phia_Growthrate.percent_Cu_vs_Fe %>% 
  mutate(Analysis = "phia_interaction", Data = "Growthrate.percent",test_intrctn = "Cu_vs_Fe", tested = rownames(phia_Growthrate.percent_Cu_vs_Fe))

phia_Growthrate.percent_Cu_vs_Fe <- data.frame(phia_Growthrate.percent_Cu_vs_Fe[,6:9], phia_Growthrate.percent_Cu_vs_Fe[, 1:5])

#~~~~~~~~~~~~~~
#Species vs Fe
phia_Growthrate.percent_Species_vs_Fe <- testInteractions(lm_Growthrate.percent, fixed="Species", across="Fe.level")
phia_Growthrate.percent_Species_vs_Fe <- phia_Growthrate.percent_Species_vs_Fe %>% 
  mutate(Analysis = "phia_interaction", Data = "Growthrate.percent",test_intrctn = "Species_vs_Fe", tested = rownames(phia_Growthrate.percent_Species_vs_Fe))

phia_Growthrate.percent_Species_vs_Fe <- data.frame(phia_Growthrate.percent_Species_vs_Fe[,6:9], phia_Growthrate.percent_Species_vs_Fe[, 1:5])

#~~~~~~~~~~~~~~
#Fe vs Species
phia_Growthrate.percent_Fe_vs_Species <- testInteractions(lm_Growthrate.percent, fixed="Fe.level", across="Species")
phia_Growthrate.percent_Fe_vs_Species <- phia_Growthrate.percent_Fe_vs_Species %>% 
  mutate(Analysis = "phia_interaction", Data = "Growthrate.percent",test_intrctn = "Fe_vs_Species", tested = rownames(phia_Growthrate.percent_Fe_vs_Species))

phia_Growthrate.percent_Fe_vs_Species <- data.frame(phia_Growthrate.percent_Fe_vs_Species[,6:9], phia_Growthrate.percent_Fe_vs_Species[, 1:5])

#~~~~~~~~~~~~~~
#Species vs Cu
phia_Growthrate.percent_Species_vs_Cu <- testInteractions(lm_Growthrate.percent, fixed="Species", across="Cu.level")
phia_Growthrate.percent_Species_vs_Cu <- phia_Growthrate.percent_Species_vs_Cu %>% 
  mutate(Analysis = "phia_interaction", Data = "Growthrate.percent",test_intrctn = "Species_vs_Cu", tested = rownames(phia_Growthrate.percent_Species_vs_Cu))

phia_Growthrate.percent_Species_vs_Cu <- data.frame(phia_Growthrate.percent_Species_vs_Cu[,6:9], phia_Growthrate.percent_Species_vs_Cu[, 1:5])

#~~~~~~~~~~~~~~
#Cu vs Species
phia_Growthrate.percent_Cu_vs_Species <- testInteractions(lm_Growthrate.percent, fixed="Cu.level", across="Species")
phia_Growthrate.percent_Cu_vs_Species <- phia_Growthrate.percent_Cu_vs_Species %>% 
  mutate(Analysis = "phia_interaction", Data = "Growthrate.percent",test_intrctn = "Cu_vs_Species", tested = rownames(phia_Growthrate.percent_Cu_vs_Species))

phia_Growthrate.percent_Cu_vs_Species <- data.frame(phia_Growthrate.percent_Cu_vs_Species[,6:9], phia_Growthrate.percent_Cu_vs_Species[, 1:5])

#~~~~~~~~~~~~~~~~~~~

#making the big Phia_Growthrate.percent table

all_phia_Growthrate.percent <- bind_rows(phia_Growthrate.percent_Cu_vs_Species, phia_Growthrate.percent_Species_vs_Cu, phia_Growthrate.percent_Fe_vs_Species, phia_Growthrate.percent_Species_vs_Fe, phia_Growthrate.percent_Cu_vs_Fe, phia_Growthrate.percent_Fe_vs_Cu, phia_Growthrate.percent_Fe_Cu_vs_Species, phia_Growthrate.percent_Species_Fe_vs_Cu, phia_Growthrate.percent_Species_Cu_vs_Fe)

```

####Now for FvFm

```{r stat_SummaryTable_FvFm, eval = FALSE}

lm_FvFm <- lm(data = mydata, FvFm.old ~ (Species + Fe.level + Cu.level)^2 - Species:Fe.level)
#~~~~~~~~~~~~~~
anova_FvFm <- anova(lm_FvFm)
anova_FvFm <- anova_FvFm %>% 
  mutate(Analysis = "anova", Data = "FvFm", Effects_Tested = rownames(anova_FvFm))

anova_FvFm <- data.frame(anova_FvFm[, 6:8], anova_FvFm[,1:5])
#~~~~~~~~~~~~~~
phia_FvFm_Species_Cu_vs_Fe <- testInteractions(lm_FvFm, fixed=c("Species", "Cu.level"), across="Fe.level")
phia_FvFm_Species_Cu_vs_Fe <- phia_FvFm_Species_Cu_vs_Fe %>% 
  mutate(Analysis = "phia_interaction", Data = "FvFm",test_intrctn = "Species_Cu_vs_Fe", tested = rownames(phia_FvFm_Species_Cu_vs_Fe))

phia_FvFm_Species_Cu_vs_Fe <- data.frame(phia_FvFm_Species_Cu_vs_Fe[,6:9], phia_FvFm_Species_Cu_vs_Fe[, 1:5])
#~~~~~~~~~~~~~~

phia_FvFm_Species_Fe_vs_Cu <- testInteractions(lm_FvFm, fixed=c("Species", "Fe.level"), across="Cu.level")
phia_FvFm_Species_Fe_vs_Cu <- phia_FvFm_Species_Fe_vs_Cu %>% 
  mutate(Analysis = "phia_interaction", Data = "FvFm",test_intrctn = "Species_Fe_vs_Cu", tested = rownames(phia_FvFm_Species_Fe_vs_Cu))

phia_FvFm_Species_Fe_vs_Cu <- data.frame(phia_FvFm_Species_Fe_vs_Cu[,6:9], phia_FvFm_Species_Fe_vs_Cu[, 1:5])

#~~~~~~~~~~~~~~

phia_FvFm_Fe_Cu_vs_Species <- testInteractions(lm_FvFm, fixed=c("Fe.level", "Cu.level"), across="Species")
phia_FvFm_Fe_Cu_vs_Species <- phia_FvFm_Fe_Cu_vs_Species %>% 
  mutate(Analysis = "phia_interaction", Data = "FvFm",test_intrctn = "Fe_Cu_vs_Species", tested = rownames(phia_FvFm_Fe_Cu_vs_Species))

phia_FvFm_Fe_Cu_vs_Species <- data.frame(phia_FvFm_Fe_Cu_vs_Species[,6:9], phia_FvFm_Fe_Cu_vs_Species[, 1:5])

#~~~~~~~~~~~~~~
#Fe vs Cu
phia_FvFm_Fe_vs_Cu <- testInteractions(lm_FvFm, fixed="Fe.level", across="Cu.level")
phia_FvFm_Fe_vs_Cu <- phia_FvFm_Fe_vs_Cu %>% 
  mutate(Analysis = "phia_interaction", Data = "FvFm",test_intrctn = "Fe_vs_Cu", tested = rownames(phia_FvFm_Fe_vs_Cu))

phia_FvFm_Fe_vs_Cu <- data.frame(phia_FvFm_Fe_vs_Cu[,6:9], phia_FvFm_Fe_vs_Cu[, 1:5])
#~~~~~~~~~~~~~~
#Cu vs Fe
phia_FvFm_Cu_vs_Fe <- testInteractions(lm_FvFm, fixed="Cu.level", across="Fe.level")
phia_FvFm_Cu_vs_Fe <- phia_FvFm_Cu_vs_Fe %>% 
  mutate(Analysis = "phia_interaction", Data = "FvFm",test_intrctn = "Cu_vs_Fe", tested = rownames(phia_FvFm_Cu_vs_Fe))

phia_FvFm_Cu_vs_Fe <- data.frame(phia_FvFm_Cu_vs_Fe[,6:9], phia_FvFm_Cu_vs_Fe[, 1:5])

#~~~~~~~~~~~~~~
#Species vs Fe
phia_FvFm_Species_vs_Fe <- testInteractions(lm_FvFm, fixed="Species", across="Fe.level")
phia_FvFm_Species_vs_Fe <- phia_FvFm_Species_vs_Fe %>% 
  mutate(Analysis = "phia_interaction", Data = "FvFm",test_intrctn = "Species_vs_Fe", tested = rownames(phia_FvFm_Species_vs_Fe))

phia_FvFm_Species_vs_Fe <- data.frame(phia_FvFm_Species_vs_Fe[,6:9], phia_FvFm_Species_vs_Fe[, 1:5])

#~~~~~~~~~~~~~~
#Fe vs Species
phia_FvFm_Fe_vs_Species <- testInteractions(lm_FvFm, fixed="Fe.level", across="Species")
phia_FvFm_Fe_vs_Species <- phia_FvFm_Fe_vs_Species %>% 
  mutate(Analysis = "phia_interaction", Data = "FvFm",test_intrctn = "Fe_vs_Species", tested = rownames(phia_FvFm_Fe_vs_Species))

phia_FvFm_Fe_vs_Species <- data.frame(phia_FvFm_Fe_vs_Species[,6:9], phia_FvFm_Fe_vs_Species[, 1:5])

#~~~~~~~~~~~~~~
#Species vs Cu
phia_FvFm_Species_vs_Cu <- testInteractions(lm_FvFm, fixed="Species", across="Cu.level")
phia_FvFm_Species_vs_Cu <- phia_FvFm_Species_vs_Cu %>% 
  mutate(Analysis = "phia_interaction", Data = "FvFm",test_intrctn = "Species_vs_Cu", tested = rownames(phia_FvFm_Species_vs_Cu))

phia_FvFm_Species_vs_Cu <- data.frame(phia_FvFm_Species_vs_Cu[,6:9], phia_FvFm_Species_vs_Cu[, 1:5])

#~~~~~~~~~~~~~~
#Cu vs Species
phia_FvFm_Cu_vs_Species <- testInteractions(lm_FvFm, fixed="Cu.level", across="Species")
phia_FvFm_Cu_vs_Species <- phia_FvFm_Cu_vs_Species %>% 
  mutate(Analysis = "phia_interaction", Data = "FvFm",test_intrctn = "Cu_vs_Species", tested = rownames(phia_FvFm_Cu_vs_Species))

phia_FvFm_Cu_vs_Species <- data.frame(phia_FvFm_Cu_vs_Species[,6:9], phia_FvFm_Cu_vs_Species[, 1:5])

#~~~~~~~~~~~~~~~~~~~

#making the big Phia_FvFm table

all_phia_FvFm <- bind_rows(phia_FvFm_Cu_vs_Species, phia_FvFm_Species_vs_Cu, phia_FvFm_Fe_vs_Species, phia_FvFm_Species_vs_Fe, phia_FvFm_Cu_vs_Fe, phia_FvFm_Fe_vs_Cu, phia_FvFm_Fe_Cu_vs_Species, phia_FvFm_Species_Fe_vs_Cu, phia_FvFm_Species_Cu_vs_Fe)

```

####Now for Sigma

```{r stat_SummaryTable_Sigma, eval = FALSE}
lm_Sigma <- lm(data = mydata, Sig.old ~ (Species + Fe.level + Cu.level)^2 - Fe.level:Cu.level)

#~~~~~~~~~~~~~~
anova_Sigma <- anova(lm_Sigma)
anova_Sigma <- anova_Sigma %>% 
  mutate(Analysis = "anova", Data = "Sigma", Effects_Tested = rownames(anova_Sigma))

anova_Sigma <- data.frame(anova_Sigma[, 6:8], anova_Sigma[,1:5])
#~~~~~~~~~~~~~~
phia_Sigma_Species_Cu_vs_Fe <- testInteractions(lm_Sigma, fixed=c("Species", "Cu.level"), across="Fe.level")
phia_Sigma_Species_Cu_vs_Fe <- phia_Sigma_Species_Cu_vs_Fe %>% 
  mutate(Analysis = "phia_interaction", Data = "Sigma",test_intrctn = "Species_Cu_vs_Fe", tested = rownames(phia_Sigma_Species_Cu_vs_Fe))

phia_Sigma_Species_Cu_vs_Fe <- data.frame(phia_Sigma_Species_Cu_vs_Fe[,6:9], phia_Sigma_Species_Cu_vs_Fe[, 1:5])
#~~~~~~~~~~~~~~

phia_Sigma_Species_Fe_vs_Cu <- testInteractions(lm_Sigma, fixed=c("Species", "Fe.level"), across="Cu.level")
phia_Sigma_Species_Fe_vs_Cu <- phia_Sigma_Species_Fe_vs_Cu %>% 
  mutate(Analysis = "phia_interaction", Data = "Sigma",test_intrctn = "Species_Fe_vs_Cu", tested = rownames(phia_Sigma_Species_Fe_vs_Cu))

phia_Sigma_Species_Fe_vs_Cu <- data.frame(phia_Sigma_Species_Fe_vs_Cu[,6:9], phia_Sigma_Species_Fe_vs_Cu[, 1:5])

#~~~~~~~~~~~~~~

phia_Sigma_Fe_Cu_vs_Species <- testInteractions(lm_Sigma, fixed=c("Fe.level", "Cu.level"), across="Species")
phia_Sigma_Fe_Cu_vs_Species <- phia_Sigma_Fe_Cu_vs_Species %>% 
  mutate(Analysis = "phia_interaction", Data = "Sigma",test_intrctn = "Fe_Cu_vs_Species", tested = rownames(phia_Sigma_Fe_Cu_vs_Species))

phia_Sigma_Fe_Cu_vs_Species <- data.frame(phia_Sigma_Fe_Cu_vs_Species[,6:9], phia_Sigma_Fe_Cu_vs_Species[, 1:5])

#~~~~~~~~~~~~~~
#Fe vs Cu
phia_Sigma_Fe_vs_Cu <- testInteractions(lm_Sigma, fixed="Fe.level", across="Cu.level")
phia_Sigma_Fe_vs_Cu <- phia_Sigma_Fe_vs_Cu %>% 
  mutate(Analysis = "phia_interaction", Data = "Sigma",test_intrctn = "Fe_vs_Cu", tested = rownames(phia_Sigma_Fe_vs_Cu))

phia_Sigma_Fe_vs_Cu <- data.frame(phia_Sigma_Fe_vs_Cu[,6:9], phia_Sigma_Fe_vs_Cu[, 1:5])
#~~~~~~~~~~~~~~
#Cu vs Fe
phia_Sigma_Cu_vs_Fe <- testInteractions(lm_Sigma, fixed="Cu.level", across="Fe.level")
phia_Sigma_Cu_vs_Fe <- phia_Sigma_Cu_vs_Fe %>% 
  mutate(Analysis = "phia_interaction", Data = "Sigma",test_intrctn = "Cu_vs_Fe", tested = rownames(phia_Sigma_Cu_vs_Fe))

phia_Sigma_Cu_vs_Fe <- data.frame(phia_Sigma_Cu_vs_Fe[,6:9], phia_Sigma_Cu_vs_Fe[, 1:5])

#~~~~~~~~~~~~~~
#Species vs Fe
phia_Sigma_Species_vs_Fe <- testInteractions(lm_Sigma, fixed="Species", across="Fe.level")
phia_Sigma_Species_vs_Fe <- phia_Sigma_Species_vs_Fe %>% 
  mutate(Analysis = "phia_interaction", Data = "Sigma",test_intrctn = "Species_vs_Fe", tested = rownames(phia_Sigma_Species_vs_Fe))

phia_Sigma_Species_vs_Fe <- data.frame(phia_Sigma_Species_vs_Fe[,6:9], phia_Sigma_Species_vs_Fe[, 1:5])

#~~~~~~~~~~~~~~
#Fe vs Species
phia_Sigma_Fe_vs_Species <- testInteractions(lm_Sigma, fixed="Fe.level", across="Species")
phia_Sigma_Fe_vs_Species <- phia_Sigma_Fe_vs_Species %>% 
  mutate(Analysis = "phia_interaction", Data = "Sigma",test_intrctn = "Fe_vs_Species", tested = rownames(phia_Sigma_Fe_vs_Species))

phia_Sigma_Fe_vs_Species <- data.frame(phia_Sigma_Fe_vs_Species[,6:9], phia_Sigma_Fe_vs_Species[, 1:5])

#~~~~~~~~~~~~~~
#Species vs Cu
phia_Sigma_Species_vs_Cu <- testInteractions(lm_Sigma, fixed="Species", across="Cu.level")
phia_Sigma_Species_vs_Cu <- phia_Sigma_Species_vs_Cu %>% 
  mutate(Analysis = "phia_interaction", Data = "Sigma",test_intrctn = "Species_vs_Cu", tested = rownames(phia_Sigma_Species_vs_Cu))

phia_Sigma_Species_vs_Cu <- data.frame(phia_Sigma_Species_vs_Cu[,6:9], phia_Sigma_Species_vs_Cu[, 1:5])

#~~~~~~~~~~~~~~
#Cu vs Species
phia_Sigma_Cu_vs_Species <- testInteractions(lm_Sigma, fixed="Cu.level", across="Species")
phia_Sigma_Cu_vs_Species <- phia_Sigma_Cu_vs_Species %>% 
  mutate(Analysis = "phia_interaction", Data = "Sigma",test_intrctn = "Cu_vs_Species", tested = rownames(phia_Sigma_Cu_vs_Species))

phia_Sigma_Cu_vs_Species <- data.frame(phia_Sigma_Cu_vs_Species[,6:9], phia_Sigma_Cu_vs_Species[, 1:5])

#~~~~~~~~~~~~~~~~~~~

#making the big Phia_Sigma table

all_phia_Sigma <- bind_rows(phia_Sigma_Cu_vs_Species, phia_Sigma_Species_vs_Cu, phia_Sigma_Fe_vs_Species, phia_Sigma_Species_vs_Fe, phia_Sigma_Cu_vs_Fe, phia_Sigma_Fe_vs_Cu, phia_Sigma_Fe_Cu_vs_Species, phia_Sigma_Species_Fe_vs_Cu, phia_Sigma_Species_Cu_vs_Fe)

```


####Now for PQ

```{r stat_SummaryTable_PQ, eval = FALSE}

lm_PQ <- lm(data = mydata, PQ_Siz.old ~ (Species + Fe.level + Cu.level)^2 - Fe.level:Cu.level - Species:Fe.level)

#~~~~~~~~~~~~~~
anova_PQ <- anova(lm_PQ)
anova_PQ <- anova_PQ %>% 
  mutate(Analysis = "anova", Data = "PQ", Effects_Tested = rownames(anova_PQ))

anova_PQ <- data.frame(anova_PQ[, 6:8], anova_PQ[,1:5])
#~~~~~~~~~~~~~~
phia_PQ_Species_Cu_vs_Fe <- testInteractions(lm_PQ, fixed=c("Species", "Cu.level"), across="Fe.level")
phia_PQ_Species_Cu_vs_Fe <- phia_PQ_Species_Cu_vs_Fe %>% 
  mutate(Analysis = "phia_interaction", Data = "PQ",test_intrctn = "Species_Cu_vs_Fe", tested = rownames(phia_PQ_Species_Cu_vs_Fe))

phia_PQ_Species_Cu_vs_Fe <- data.frame(phia_PQ_Species_Cu_vs_Fe[,6:9], phia_PQ_Species_Cu_vs_Fe[, 1:5])
#~~~~~~~~~~~~~~

phia_PQ_Species_Fe_vs_Cu <- testInteractions(lm_PQ, fixed=c("Species", "Fe.level"), across="Cu.level")
phia_PQ_Species_Fe_vs_Cu <- phia_PQ_Species_Fe_vs_Cu %>% 
  mutate(Analysis = "phia_interaction", Data = "PQ",test_intrctn = "Species_Fe_vs_Cu", tested = rownames(phia_PQ_Species_Fe_vs_Cu))

phia_PQ_Species_Fe_vs_Cu <- data.frame(phia_PQ_Species_Fe_vs_Cu[,6:9], phia_PQ_Species_Fe_vs_Cu[, 1:5])

#~~~~~~~~~~~~~~

phia_PQ_Fe_Cu_vs_Species <- testInteractions(lm_PQ, fixed=c("Fe.level", "Cu.level"), across="Species")
phia_PQ_Fe_Cu_vs_Species <- phia_PQ_Fe_Cu_vs_Species %>% 
  mutate(Analysis = "phia_interaction", Data = "PQ",test_intrctn = "Fe_Cu_vs_Species", tested = rownames(phia_PQ_Fe_Cu_vs_Species))

phia_PQ_Fe_Cu_vs_Species <- data.frame(phia_PQ_Fe_Cu_vs_Species[,6:9], phia_PQ_Fe_Cu_vs_Species[, 1:5])

#~~~~~~~~~~~~~~
#Fe vs Cu
phia_PQ_Fe_vs_Cu <- testInteractions(lm_PQ, fixed="Fe.level", across="Cu.level")
phia_PQ_Fe_vs_Cu <- phia_PQ_Fe_vs_Cu %>% 
  mutate(Analysis = "phia_interaction", Data = "PQ",test_intrctn = "Fe_vs_Cu", tested = rownames(phia_PQ_Fe_vs_Cu))

phia_PQ_Fe_vs_Cu <- data.frame(phia_PQ_Fe_vs_Cu[,6:9], phia_PQ_Fe_vs_Cu[, 1:5])
#~~~~~~~~~~~~~~
#Cu vs Fe
phia_PQ_Cu_vs_Fe <- testInteractions(lm_PQ, fixed="Cu.level", across="Fe.level")
phia_PQ_Cu_vs_Fe <- phia_PQ_Cu_vs_Fe %>% 
  mutate(Analysis = "phia_interaction", Data = "PQ",test_intrctn = "Cu_vs_Fe", tested = rownames(phia_PQ_Cu_vs_Fe))

phia_PQ_Cu_vs_Fe <- data.frame(phia_PQ_Cu_vs_Fe[,6:9], phia_PQ_Cu_vs_Fe[, 1:5])

#~~~~~~~~~~~~~~
#Species vs Fe
phia_PQ_Species_vs_Fe <- testInteractions(lm_PQ, fixed="Species", across="Fe.level")
phia_PQ_Species_vs_Fe <- phia_PQ_Species_vs_Fe %>% 
  mutate(Analysis = "phia_interaction", Data = "PQ",test_intrctn = "Species_vs_Fe", tested = rownames(phia_PQ_Species_vs_Fe))

phia_PQ_Species_vs_Fe <- data.frame(phia_PQ_Species_vs_Fe[,6:9], phia_PQ_Species_vs_Fe[, 1:5])

#~~~~~~~~~~~~~~
#Fe vs Species
phia_PQ_Fe_vs_Species <- testInteractions(lm_PQ, fixed="Fe.level", across="Species")
phia_PQ_Fe_vs_Species <- phia_PQ_Fe_vs_Species %>% 
  mutate(Analysis = "phia_interaction", Data = "PQ",test_intrctn = "Fe_vs_Species", tested = rownames(phia_PQ_Fe_vs_Species))

phia_PQ_Fe_vs_Species <- data.frame(phia_PQ_Fe_vs_Species[,6:9], phia_PQ_Fe_vs_Species[, 1:5])

#~~~~~~~~~~~~~~
#Species vs Cu
phia_PQ_Species_vs_Cu <- testInteractions(lm_PQ, fixed="Species", across="Cu.level")
phia_PQ_Species_vs_Cu <- phia_PQ_Species_vs_Cu %>% 
  mutate(Analysis = "phia_interaction", Data = "PQ",test_intrctn = "Species_vs_Cu", tested = rownames(phia_PQ_Species_vs_Cu))

phia_PQ_Species_vs_Cu <- data.frame(phia_PQ_Species_vs_Cu[,6:9], phia_PQ_Species_vs_Cu[, 1:5])

#~~~~~~~~~~~~~~
#Cu vs Species
phia_PQ_Cu_vs_Species <- testInteractions(lm_PQ, fixed="Cu.level", across="Species")
phia_PQ_Cu_vs_Species <- phia_PQ_Cu_vs_Species %>% 
  mutate(Analysis = "phia_interaction", Data = "PQ",test_intrctn = "Cu_vs_Species", tested = rownames(phia_PQ_Cu_vs_Species))

phia_PQ_Cu_vs_Species <- data.frame(phia_PQ_Cu_vs_Species[,6:9], phia_PQ_Cu_vs_Species[, 1:5])

#~~~~~~~~~~~~~~~~~~~

#making the big Phia_PQ table

all_phia_PQ <- bind_rows(phia_PQ_Cu_vs_Species, phia_PQ_Species_vs_Cu, phia_PQ_Fe_vs_Species, phia_PQ_Species_vs_Fe, phia_PQ_Cu_vs_Fe, phia_PQ_Fe_vs_Cu, phia_PQ_Fe_Cu_vs_Species, phia_PQ_Species_Fe_vs_Cu, phia_PQ_Species_Cu_vs_Fe)

```

####Now for Chla

```{r stat_SummaryTable_Chla, eval = FALSE}
lm_Chla <- lm (data = mydata, Chla.per.cell.vol.fg.fL ~ (Species * Fe.level * Cu.level)) # Yes, this is the same as before. I leave it as is

#~~~~~~~~~~~~~~
anova_Chla <- anova(lm_Chla)
anova_Chla <- anova_Chla %>% 
  mutate(Analysis = "anova", Data = "Chla", Effects_Tested = rownames(anova_Chla))

anova_Chla <- data.frame(anova_Chla[, 6:8], anova_Chla[,1:5])
#~~~~~~~~~~~~~~
phia_Chla_Species_Cu_vs_Fe <- testInteractions(lm_Chla, fixed=c("Species", "Cu.level"), across="Fe.level")
phia_Chla_Species_Cu_vs_Fe <- phia_Chla_Species_Cu_vs_Fe %>% 
  mutate(Analysis = "phia_interaction", Data = "Chla",test_intrctn = "Species_Cu_vs_Fe", tested = rownames(phia_Chla_Species_Cu_vs_Fe))

phia_Chla_Species_Cu_vs_Fe <- data.frame(phia_Chla_Species_Cu_vs_Fe[,6:9], phia_Chla_Species_Cu_vs_Fe[, 1:5])
#~~~~~~~~~~~~~~

phia_Chla_Species_Fe_vs_Cu <- testInteractions(lm_Chla, fixed=c("Species", "Fe.level"), across="Cu.level")
phia_Chla_Species_Fe_vs_Cu <- phia_Chla_Species_Fe_vs_Cu %>% 
  mutate(Analysis = "phia_interaction", Data = "Chla",test_intrctn = "Species_Fe_vs_Cu", tested = rownames(phia_Chla_Species_Fe_vs_Cu))

phia_Chla_Species_Fe_vs_Cu <- data.frame(phia_Chla_Species_Fe_vs_Cu[,6:9], phia_Chla_Species_Fe_vs_Cu[, 1:5])

#~~~~~~~~~~~~~~

phia_Chla_Fe_Cu_vs_Species <- testInteractions(lm_Chla, fixed=c("Fe.level", "Cu.level"), across="Species")
phia_Chla_Fe_Cu_vs_Species <- phia_Chla_Fe_Cu_vs_Species %>% 
  mutate(Analysis = "phia_interaction", Data = "Chla",test_intrctn = "Fe_Cu_vs_Species", tested = rownames(phia_Chla_Fe_Cu_vs_Species))

phia_Chla_Fe_Cu_vs_Species <- data.frame(phia_Chla_Fe_Cu_vs_Species[,6:9], phia_Chla_Fe_Cu_vs_Species[, 1:5])

#~~~~~~~~~~~~~~
#Fe vs Cu
phia_Chla_Fe_vs_Cu <- testInteractions(lm_Chla, fixed="Fe.level", across="Cu.level")
phia_Chla_Fe_vs_Cu <- phia_Chla_Fe_vs_Cu %>% 
  mutate(Analysis = "phia_interaction", Data = "Chla",test_intrctn = "Fe_vs_Cu", tested = rownames(phia_Chla_Fe_vs_Cu))

phia_Chla_Fe_vs_Cu <- data.frame(phia_Chla_Fe_vs_Cu[,6:9], phia_Chla_Fe_vs_Cu[, 1:5])
#~~~~~~~~~~~~~~
#Cu vs Fe
phia_Chla_Cu_vs_Fe <- testInteractions(lm_Chla, fixed="Cu.level", across="Fe.level")
phia_Chla_Cu_vs_Fe <- phia_Chla_Cu_vs_Fe %>% 
  mutate(Analysis = "phia_interaction", Data = "Chla",test_intrctn = "Cu_vs_Fe", tested = rownames(phia_Chla_Cu_vs_Fe))

phia_Chla_Cu_vs_Fe <- data.frame(phia_Chla_Cu_vs_Fe[,6:9], phia_Chla_Cu_vs_Fe[, 1:5])

#~~~~~~~~~~~~~~
#Species vs Fe
phia_Chla_Species_vs_Fe <- testInteractions(lm_Chla, fixed="Species", across="Fe.level")
phia_Chla_Species_vs_Fe <- phia_Chla_Species_vs_Fe %>% 
  mutate(Analysis = "phia_interaction", Data = "Chla",test_intrctn = "Species_vs_Fe", tested = rownames(phia_Chla_Species_vs_Fe))

phia_Chla_Species_vs_Fe <- data.frame(phia_Chla_Species_vs_Fe[,6:9], phia_Chla_Species_vs_Fe[, 1:5])

#~~~~~~~~~~~~~~
#Fe vs Species
phia_Chla_Fe_vs_Species <- testInteractions(lm_Chla, fixed="Fe.level", across="Species")
phia_Chla_Fe_vs_Species <- phia_Chla_Fe_vs_Species %>% 
  mutate(Analysis = "phia_interaction", Data = "Chla",test_intrctn = "Fe_vs_Species", tested = rownames(phia_Chla_Fe_vs_Species))

phia_Chla_Fe_vs_Species <- data.frame(phia_Chla_Fe_vs_Species[,6:9], phia_Chla_Fe_vs_Species[, 1:5])

#~~~~~~~~~~~~~~
#Species vs Cu
phia_Chla_Species_vs_Cu <- testInteractions(lm_Chla, fixed="Species", across="Cu.level")
phia_Chla_Species_vs_Cu <- phia_Chla_Species_vs_Cu %>% 
  mutate(Analysis = "phia_interaction", Data = "Chla",test_intrctn = "Species_vs_Cu", tested = rownames(phia_Chla_Species_vs_Cu))

phia_Chla_Species_vs_Cu <- data.frame(phia_Chla_Species_vs_Cu[,6:9], phia_Chla_Species_vs_Cu[, 1:5])

#~~~~~~~~~~~~~~
#Cu vs Species
phia_Chla_Cu_vs_Species <- testInteractions(lm_Chla, fixed="Cu.level", across="Species")
phia_Chla_Cu_vs_Species <- phia_Chla_Cu_vs_Species %>% 
  mutate(Analysis = "phia_interaction", Data = "Chla",test_intrctn = "Cu_vs_Species", tested = rownames(phia_Chla_Cu_vs_Species))

phia_Chla_Cu_vs_Species <- data.frame(phia_Chla_Cu_vs_Species[,6:9], phia_Chla_Cu_vs_Species[, 1:5])

#~~~~~~~~~~~~~~~~~~~

#making the big Phia_Chla table

all_phia_Chla <- bind_rows(phia_Chla_Cu_vs_Species, phia_Chla_Species_vs_Cu, phia_Chla_Fe_vs_Species, phia_Chla_Species_vs_Fe, phia_Chla_Cu_vs_Fe, phia_Chla_Fe_vs_Cu, phia_Chla_Fe_Cu_vs_Species, phia_Chla_Species_Fe_vs_Cu, phia_Chla_Species_Cu_vs_Fe)

```

####Now for Chla.cell

```{r stat_SummaryTable_Chla.cell, eval = FALSE}
lm_Chla.cell <- lm (data = mydata, Chla.per.cell.pg.cell ~ (Species * Fe.level * Cu.level)) # Yes, this is the same as before. I leave it as is

#~~~~~~~~~~~~~~
anova_Chla <- anova(lm_Chla)
anova_Chla <- anova_Chla %>% 
  mutate(Analysis = "anova", Data = "Chla", Effects_Tested = rownames(anova_Chla))

anova_Chla <- data.frame(anova_Chla[, 6:8], anova_Chla[,1:5])
#~~~~~~~~~~~~~~
phia_Chla_Species_Cu_vs_Fe <- testInteractions(lm_Chla, fixed=c("Species", "Cu.level"), across="Fe.level")
phia_Chla_Species_Cu_vs_Fe <- phia_Chla_Species_Cu_vs_Fe %>% 
  mutate(Analysis = "phia_interaction", Data = "Chla",test_intrctn = "Species_Cu_vs_Fe", tested = rownames(phia_Chla_Species_Cu_vs_Fe))

phia_Chla_Species_Cu_vs_Fe <- data.frame(phia_Chla_Species_Cu_vs_Fe[,6:9], phia_Chla_Species_Cu_vs_Fe[, 1:5])
#~~~~~~~~~~~~~~

phia_Chla_Species_Fe_vs_Cu <- testInteractions(lm_Chla, fixed=c("Species", "Fe.level"), across="Cu.level")
phia_Chla_Species_Fe_vs_Cu <- phia_Chla_Species_Fe_vs_Cu %>% 
  mutate(Analysis = "phia_interaction", Data = "Chla",test_intrctn = "Species_Fe_vs_Cu", tested = rownames(phia_Chla_Species_Fe_vs_Cu))

phia_Chla_Species_Fe_vs_Cu <- data.frame(phia_Chla_Species_Fe_vs_Cu[,6:9], phia_Chla_Species_Fe_vs_Cu[, 1:5])

#~~~~~~~~~~~~~~

phia_Chla_Fe_Cu_vs_Species <- testInteractions(lm_Chla, fixed=c("Fe.level", "Cu.level"), across="Species")
phia_Chla_Fe_Cu_vs_Species <- phia_Chla_Fe_Cu_vs_Species %>% 
  mutate(Analysis = "phia_interaction", Data = "Chla",test_intrctn = "Fe_Cu_vs_Species", tested = rownames(phia_Chla_Fe_Cu_vs_Species))

phia_Chla_Fe_Cu_vs_Species <- data.frame(phia_Chla_Fe_Cu_vs_Species[,6:9], phia_Chla_Fe_Cu_vs_Species[, 1:5])

#~~~~~~~~~~~~~~
#Fe vs Cu
phia_Chla_Fe_vs_Cu <- testInteractions(lm_Chla, fixed="Fe.level", across="Cu.level")
phia_Chla_Fe_vs_Cu <- phia_Chla_Fe_vs_Cu %>% 
  mutate(Analysis = "phia_interaction", Data = "Chla",test_intrctn = "Fe_vs_Cu", tested = rownames(phia_Chla_Fe_vs_Cu))

phia_Chla_Fe_vs_Cu <- data.frame(phia_Chla_Fe_vs_Cu[,6:9], phia_Chla_Fe_vs_Cu[, 1:5])
#~~~~~~~~~~~~~~
#Cu vs Fe
phia_Chla_Cu_vs_Fe <- testInteractions(lm_Chla, fixed="Cu.level", across="Fe.level")
phia_Chla_Cu_vs_Fe <- phia_Chla_Cu_vs_Fe %>% 
  mutate(Analysis = "phia_interaction", Data = "Chla",test_intrctn = "Cu_vs_Fe", tested = rownames(phia_Chla_Cu_vs_Fe))

phia_Chla_Cu_vs_Fe <- data.frame(phia_Chla_Cu_vs_Fe[,6:9], phia_Chla_Cu_vs_Fe[, 1:5])

#~~~~~~~~~~~~~~
#Species vs Fe
phia_Chla_Species_vs_Fe <- testInteractions(lm_Chla, fixed="Species", across="Fe.level")
phia_Chla_Species_vs_Fe <- phia_Chla_Species_vs_Fe %>% 
  mutate(Analysis = "phia_interaction", Data = "Chla",test_intrctn = "Species_vs_Fe", tested = rownames(phia_Chla_Species_vs_Fe))

phia_Chla_Species_vs_Fe <- data.frame(phia_Chla_Species_vs_Fe[,6:9], phia_Chla_Species_vs_Fe[, 1:5])

#~~~~~~~~~~~~~~
#Fe vs Species
phia_Chla_Fe_vs_Species <- testInteractions(lm_Chla, fixed="Fe.level", across="Species")
phia_Chla_Fe_vs_Species <- phia_Chla_Fe_vs_Species %>% 
  mutate(Analysis = "phia_interaction", Data = "Chla",test_intrctn = "Fe_vs_Species", tested = rownames(phia_Chla_Fe_vs_Species))

phia_Chla_Fe_vs_Species <- data.frame(phia_Chla_Fe_vs_Species[,6:9], phia_Chla_Fe_vs_Species[, 1:5])

#~~~~~~~~~~~~~~
#Species vs Cu
phia_Chla_Species_vs_Cu <- testInteractions(lm_Chla, fixed="Species", across="Cu.level")
phia_Chla_Species_vs_Cu <- phia_Chla_Species_vs_Cu %>% 
  mutate(Analysis = "phia_interaction", Data = "Chla",test_intrctn = "Species_vs_Cu", tested = rownames(phia_Chla_Species_vs_Cu))

phia_Chla_Species_vs_Cu <- data.frame(phia_Chla_Species_vs_Cu[,6:9], phia_Chla_Species_vs_Cu[, 1:5])

#~~~~~~~~~~~~~~
#Cu vs Species
phia_Chla_Cu_vs_Species <- testInteractions(lm_Chla, fixed="Cu.level", across="Species")
phia_Chla_Cu_vs_Species <- phia_Chla_Cu_vs_Species %>% 
  mutate(Analysis = "phia_interaction", Data = "Chla",test_intrctn = "Cu_vs_Species", tested = rownames(phia_Chla_Cu_vs_Species))

phia_Chla_Cu_vs_Species <- data.frame(phia_Chla_Cu_vs_Species[,6:9], phia_Chla_Cu_vs_Species[, 1:5])

#~~~~~~~~~~~~~~~~~~~

#making the big Phia_Chla table

all_phia_Chla <- bind_rows(phia_Chla_Cu_vs_Species, phia_Chla_Species_vs_Cu, phia_Chla_Fe_vs_Species, phia_Chla_Species_vs_Fe, phia_Chla_Cu_vs_Fe, phia_Chla_Fe_vs_Cu, phia_Chla_Fe_Cu_vs_Species, phia_Chla_Species_Fe_vs_Cu, phia_Chla_Species_Cu_vs_Fe)

```

### Resources

* [Tutorial on linear regression](http://rtutorialseries.blogspot.ca/2009/11/r-tutorial-series-simple-linear.html)
* [Tutorial on multiple linear regression](http://rtutorialseries.blogspot.ca/2009/12/r-tutorial-series-multiple-linear.html)
* [Tutorial on posthoc-tests](http://rtutorialseries.blogspot.ca/2011/03/r-tutorial-series-anova-pairwise.html)

