---
title: "Meeting with Rick White"
author: "Anna A. Hippmann"
date: "May 22nd, 2015"
output: 
  html_document: 
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Libraries used
``` {r libraries, eval=TRUE}
library(lsmeans)
library(phia)
library(visreg)
library(dplyr)
library(ggplot2)
library(knitr)
```

### Overview

<a id="BackUP"></a>

* What I did with [Rick White](#RickWhite)
  + `z_all <- lm()` with all main effects and interaction - [z_all](#z_all)
  + `z <- lm()` without Species:Cu.level interaction - [z](#z)
  + `anova(z)` anova indicating where to look for significant effects and interacitons - [`anova(z)`](#anova_z)
  + `lsmeans()` to check for pairwise comparisons
    +lsmeans has changed quite a bit in newer version -> I am thinking about different post-hoc test
    
* using `phia` ("post hoc interaction association") package to check for [interaction](#phia_interaction)
* using `phia` to do [pairwise comparison](#phia_pariwise)


* Overview of [My Method](#MyMethod) to Analyze my Physiological Data
  + [Growthrate dd-1](#Growthrate.dd)
  + [Growthrate Percent](#Growthrate.percent)
  + [Fv/Fm](#FvFm)
  + [Sigma](#Sigma)
  + [PQ Size](#PQ)

* __NOT USED__
* run `lm()` only on [TO 1003](#lm_TO03)
* [Tukey HSD](#Tukey_01)

## Run Down of what we did in SCARL meeting in May 2015


I met with Rick White of SCARL at UBC to discuss my approach to analyze my physiological data statistically. The main question was, whether I would need to use a mixed effects model or a fixed effects model. Then how to actually go about analyzing it practically (i.e.which program/ package to use etc)

As per my experimental set up, I have **3 fixed effects**:

1) Species _(as I choose these 2 strains on purpose to test for differences between them)_
2) Fe-level
3) Cu-level

For this I will need to use 

1) the **function `lm()` = linear model**. 
2) then use `anova()` on the `lm object`
3) then use `lsmeans()` on the `lm object` _(to do all the different pairwise comparisons to my heart's desire)_

Let's start by loading in my data and having a look at it:

```{r data input, eval=TRUE}
#I used the original "ALL_PhysiologicalData_2015_04.txt" and added columns "Treatment" and "Merged" to it, then saved the ensuing file under "ALL_PhysiologicalData_2015_04_withMerged_Variable.txt", so I can use it for all my plots

mydata <- read.delim("ALL_PhysiologicalData_2015_04_withMerged_Variable.txt", sep="\t", header=T)

mean.df <- read.delim("Physiological_Data_Mean_Values.txt", sep="\t", header=T)

str(mydata)
```

```{r graph_Growthrate, eval=TRUE}
p <- ggplot (mydata , aes(Treatment, Growthrate.dd.1 ))
p + geom_point(aes(group=Merged, colour=Species), size = 3)+
  labs(title="", x ="")+
  geom_point(data=mean.df , aes(Treatment, Growthrate.dd.1, size=2, colour=Species), shape = 45, size = 9)+
  guides(alpha = "none", size = "none", shape = "none")

```

To really understand what we are seeing, especially with the copper data, we need to remember the different metal concentrations that are used for the different strains and treatments:

```{r tabkle metal concnetrations per treatment, eval=TRUE}
kable((read.delim("MetalConcentrationsInMedia.txt")), format = "markdown")
```

__Fe concentrations__:

If we look closely at the table above, we will see that for __both strains__, we subjected them to the __same high Fe__ concentration (__1370nmol__) and the __same low Fe__ concentration (__12.5nmol__) in the media.

__Cu concentrations - high__:

However, as per preliminary tests (_data not shown_), these two strains have different Cu requirements to sustain their respective optimal growth rates and to limit their growth rates by Cu. 
Hence, high Cu concentrations differ in the following way: __TO 1003__ requires 10.2 nmol total Cu in its growth medium under our chosen high Fe regime, whereas __TO1005__ requires more, namely __14.32 nmol total Cu__ in the control medium.

__Cu concentrations - low__:

Looking at limiting Cu concentrations, a similar scenario is seen. Where __TO 1003__ is very hard to limit with Cu, when sufficient Fe is present in the media (only background Cu is present in our study ~ __0.2 nmol Cu__), __TO 1005__ shows significant limitation at Cu levels of __6.08 nmol__. When subjected to iron / copper co-limitation, __TO 1005__ growthrate is even more limited, hinting at an interactive effect of iron and copper concentrations (which we will see further down statistically proven).
Under low Fe conditions, __TO 1003__ can not survive with only background copper concentration. Hence, we added more Cu (__1.96 nmol Cu__) under Fe-limiting conditions compared to low Cu concentrations under Fe-replete conditions (0.2 nmol). This again, shows an interdependence of Fe and Cu albeit, we don;t necessarily see it when we look at the graph, as it only states "low Cu" and "lowFeCu"without going into detail of the copper concentrations. in TO 1003, the growthrates for low Cu and low FeCu are similar so one could be misled into the interpretation that there is no real co-limitation. However, with the background information given here, it is clear that __there is also Fe-Cu-colimitation occuring in TO 1003__ (as has been shown in previous studies).


### 1) Recreating what I did with Rick White

<a id="RickWhite"></a>

[Back Up](#BackUP)

I first want to look at the growth rate and determine what influences growth rate. I will use `lm() to get a model which will take into account the different factors to predict the resulting growth rate.

__When testing for the different effects:__

* "__+__" means "_test for main effects_"
* "__:__" means "_test for interacting effects_"
* "__\*__" means "_test for both main and interacting effects_"

<a id="z_all"></a>

#### z_all - linear model chacking for all interactions and main effects

[Back Up](#BackUP)

```{r lm growthrate_allMain and Interaction, eval=TRUE}
z_all <- lm(data=mydata, Growthrate.dd.1~(Species*Fe.level*Cu.level)) #this will model the Growth rate dependend on the 
#three main effects (Species, Fe.level, Cu.level) and will include all possible interactions
summary(z_all)

```

To look at the actual differences, we need to look at the `anova` table:

```{r lm growthrate_allMain and Interaction_ANOVA, eval=TRUE}
anova(z_all) #this will use the linear model and give us a table of the analysis of the variance in our dataset

```



Looking at the ANOVA table for the linear model that test for all main effects and interactions, we see that

* __Species__ does have a significant effect on growth rate (F (1,16) = 11.67, p.val < 0.01)
* __Fe. level__ has an effect on growthrate (F (1,16) = 35.47, p.val < 0.0001)
* __Cu level__ has an effect on growthrate (F (1,16) = 152.75, p.val < 0.00001)
* there is an __interaction__ between __Species and Fe LEVEL__ (F(1,16) = 22.47, p.val = 0.0002)
    + i.e. depending on the Species the growthrate is different under similar Fe conditions
* there is NOT INTERACTION between Species and CU LEVEL
    + i.e. this is somewhat what I had aimed for as this means that both Species have a similar growthrate reduction under the same Cu.level -> this way I can see how their proteomic and physiological response is similar or different!
* there is an __interaction__ between __Fe LEVEL and Cu LEVEL__ (F(1,16) = 8.29, p.val = 0.01) 

__NOTE:__ the anova table only tells me that there are differences e.g. between the Species. IT DOES NOT TELL ME depending on what variables etc... for that we need to do pairwise comparisons.



<a id="z"></a>

### z - linear model not checking for interaction between Cu and species 

[Back Up](#BackUP)

__FIRST THOUGH__: as we saw in the `anova` table that there is __no interaction between Cu.level and Species__, we can __take the interaction term OUT__ when we make the linear model. Let's see how this will change the model


```{r lm growthrate_allMain just known interaction, eval=TRUE}
z <- lm(data=mydata, Growthrate.dd.1~(Species+Fe.level+Cu.level)^2-Species:Cu.level) #this will model the Growth rate dependend on
#three main effects (Species, Fe.level, Cu.level) and will include 
#possible interactions between Species:Fe.level, Fe.level:Cu.level 
#but NOT Species:Cu.level as we took that one out!

summary(z)
plot(z) ##these plots are diagnostic and will give indications if the assumptions are met
```

<a id="anova_z"></a>

#### Anova table of z model

[Back Up](#BackUP)

Again, we need to look at the ANOVA table:
```{r lm growthrate_allMain limited Interaction_ANOVA, eval=TRUE}
anova(z) #this will use the linear model and give us a table of the analysis of the variance in our dataset

```


Looking at the ANOVA table for the linear model that _does not_ test for interaction between Cu.level and Species, basically, we see the same significant factors and interactions as before, just with stronger significance (probably due to the higher degrees of freedom: 18 vs 16)



* __Species__ does have a significant effect on growth rate
* __Fe. level__ has an effect on growthrate
* __Cu level__ has an effect on growthrate now: (F (1,18) = 155.27, p.val <0.00001),  [*before:(F (1,16) = 152.75, p.val <0.00001)*]
* there is still an __interaction__ between __Species and Fe LEVEL__ now: (F(1,18) = 22.84, p.val = 0.000015), [*before: (F(1,16) = 22.47, p.val = 0.0002)*]
    + i.e. depending on the Species the growthrate is different under similar Fe conditions
* there is an __interaction__ between __Fe LEVEL and Cu LEVEL__ now: (F(1,18) = 8.43, p.val < 0.01), [*before: (F(1,16) = 8.29, p.val = 0.01)*] 

### What if we use the `phia` package to look into interactions or main effects?

<a id="phia_interaction"></a>

[Back Up](#BackUP)

This is basically from the tutorial / examples given in the `R` vignette by _Helios De Rosario Martinez_ ["Analysing interactions of fitted models"](https://cran.r-project.org/web/packages/phia/vignettes/phia.pdf)

[...] In factorial experiments like this one, the dependency between factor levels and the response variable is usually represented in a contingency table, where the rows and columns are related to the different levels of both treatments, and __each cell contains the adjusted mean of the response for the corresponding interaction of factors__. When there is an interaction effect, the cell means are taken as the most straightforward way of representing this effect. 

These values and their standard errors can be obtained from the model coeffients with the function `interactionMeans` in the package `phia`, using the fitted model as first (and in this case only) argument:

```{r phia_interaction means, eval=TRUE}

(mydata.means <- interactionMeans(z))
plot(mydata.means)
```

This plot shows us main effects (such as Cu.level) and first order interactions (such as Species and Fe.level). As per the "marginality principle" (see J. A. Nelder, \A reformulation of linear models," Journal of the Royal Statistical Society. Series A (General), vol. 140, no. 1, pp. 48{77, 1977.), those factors that are involved in interactions, should not be interpreted as single effects.

As we see in the upper right and lower left corner, Species and Cu really do not seem to have an interaction effect. They change in the same way (lines are parallel). However, when we look at upper middle and middle left cell, we see that growthrate changes in a different way depending on Species and Fe level. And to a much lesser extend for Fe.level and Cu.level as seen in middle right and lower middle cell.

#### Pairwise Comparisons

<a id="phia_pairwise"></a>

[Back Up](#BackUP)

In order to put actual numbers for the significant differences, I will proceed with pairwise comparisons by having a fixed factor and testing how it changes dependend on another factor

```{r phia_interaction_Contrasts_Species_Felevel, eval=TRUE}
testInteractions(z, fixed="Species", across="Fe.level")
```

This means that the two different Fe.levels I used (high and low) does not significantly change the growth rate in TO 1003 (F(1,18) = 0.75, p.val = 0.397) but it does change the growthrate significantly in TO 1005 (F(1,18) = 58.14, p-val < 0.00001))

```{r phia_interaction_Contrasts_Fe.level_Species, eval=TRUE}
testInteractions(z, fixed="Fe.level", across="Species")
```

This means that the two Species have significantly different growthrates under high Fe conditions (F(1,18), p.val < 0.0001) but are not sig different under low Fe conditions

```{r phia_interaction_Contrasts_Fe.level_Cu.level, eval=TRUE}
testInteractions(z, fixed="Fe.level", across="Cu.level")
```

This means that there is significant growthrate changes from high Cu to low Cu in both Species (F(1,18) = 118.03, p.val < 0.00001) and that the same is true under low Fe conditions, that the additional lowering of Cu.level changes growth ratessignificantly (F(1,18) = 45.67, p.val < 0.00001)

```{r phia_interaction_Contrasts_Cu.level_Fe.level, eval=TRUE}
testInteractions(z, fixed="Cu.level", across="Fe.level")
```

<a id="MyMethod"></a>

### Overview of My Method to Analyze my Physiological Data

OK, after this first inital approach (and some more down below under ["Not used"](#NotUsed)), I will settle for the following:

0) have a look at the graph of the actual data! :)
1) do a `linear model`, checking for all main and interacting effects
  + `lm(response ~ Species * Fe.level * Cu.level)`
2) do an `anova` on this `lm` object to see the F statistics and p-values
  + dependig on seen or not seen interactions, modify the `lm()` accordingly
3) then do pairwise comparisons using `phia` package to look into what is contributing how into the significant interactions seen in the `anova`

<a id="Growthrate.percent"></a>

#### Growthrate - percent of mu max

[Back Up](#BackUP)

First a look at the graph: 

```{r graph_Growthrate.percent, eval=TRUE}
p <- ggplot (mydata , aes(Treatment, Growthrate.Percent..u.umax.))
p + geom_point(aes(group=Merged, colour=Species), size = 3)+
  labs(title="", x ="")+
  geom_point(data=mean.df , aes(Treatment, Growthrate.Percent, size=2, colour=Species), shape = 45, size = 9)+
  guides(alpha = "none", size = "none", shape = "none")

```

Now we start with a linear model testing for all main effects and interactions possible:

```{r lm_all_Growthrate.percent, eval=TRUE}
lm_all_Growthrate.percent <- lm(data = mydata, Growthrate.Percent..u.umax. ~ (Species * Fe.level * Cu.level))
summary(lm_all_Growthrate.percent) # we need to look at the actual anova to knwo where we need to look further
anova(lm_all_Growthrate.percent) # this shows, we can take out the interaction between Species: Cu.level
```


```{r lm_Growthrate.percent, eval=TRUE}
lm_Growthrate.percent <- lm(data = mydata, Growthrate.Percent..u.umax. ~ (Species + Fe.level + Cu.level)^2 - Species:Cu.level)
summary(lm_Growthrate.percent) # we need to look at the actual anova to knwo where we need to look further
plot.new()
plot(lm_Growthrate.percent)

anova(lm_Growthrate.percent) # this shows, we can take out the interaction between Species: Cu.level
```

### Anova Table - Growthrate.Percent

Looking at the ANOVA table for the linear model that _does not_ test for interaction between Cu.level and Species, for the data __Growthrate Percent of umax__, we see the following significant factors:


* __Species__ is __not__ a main effect on its own
* __Fe. level__ has an effect on growthrate
* __Cu level__ has an effect on growthrate now 
* there is still an __interaction__ between __Species and Fe level now: (F(1,18) = 14.80, p.val = 0.001)
    + i.e. depending on the Species the growthrate is different under similar Fe conditions
* there is an __interaction__ between __Fe level and Cu level: (F(1,18) = 7.32, p.val = 0.02)


### Using the `phia` package to look into significant effects in growthrate percent of mu max?

Again, any main effects that are included in interacting effects will be looked at through pairwise comparisons of the interacting factors

```{r phia_interaction means_Growthrate.percent, eval=TRUE}

(Growthrate.percent.means <- interactionMeans(lm_Growthrate.percent))
plot(Growthrate.percent.means)
```

This plot shows us main effects (such as Cu.level) and first order interactions (such as Species and Fe.level). As per the "marginality principle" (see J. A. Nelder, \A reformulation of linear models," Journal of the Royal Statistical Society. Series A (General), vol. 140, no. 1, pp. 48{77, 1977.), those factors that are involved in interactions, should not be interpreted as single effects.

As we see in the upper right and lower left corner, Species and Cu really do not seem to have an interaction effect. They change in the same way (lines are parallel). However, when we look at upper middle and middle left cell, we see that growthrate changes in a different way depending on Species and Fe level. And to a much lesser extend for Fe.level and Cu.level as seen in middle right and lower middle cell.

#### Pairwise Comparisons

<a id="phia_pairwise"></a>

[Back Up](#BackUP)

In order to put actual numbers for the significant differences, I will proceed with pairwise comparisons by having a fixed factor and testing how it changes dependend on another factor

```{r phia_interaction_Contrasts_Species_Felevel_Growthrate.percent, eval=TRUE}
testInteractions(lm_Growthrate.percent, fixed="Species", across="Fe.level")
```

This means that the two different Fe.levels I used (high and low) does not significantly change the growth rate in TO 1003 (F(1,18) = 0.79, p.val = 0.39) but it does change the growthrate significantly in TO 1005 (F(1,18) = 40.05, p-val < 0.0001))

```{r phia_interaction_Contrasts_Fe.level_Species_Growthrate.percent, eval=TRUE}
testInteractions(lm_Growthrate.percent, fixed="Fe.level", across="Species")
```

This means that the two Species have no significantly different growthrates under high Fe conditions (F(1,18) = 4.02, p.val = 0.06) which makes sense as they have both umax as 100 percent and are both similarly reduced by teh given Cu.levels that they have been subjected to. Under low iron their respective growthrates are significantly different (F =  11.81, p.val = 0.006)


```{r phia_interaction_Contrasts_Fe.level_Cu.level_Growthrate.percent, eval=TRUE}
testInteractions(lm_Growthrate.percent, fixed="Fe.level", across="Cu.level")
```

This means that there is significant growthrate changes from high Cu to low Cu in both Species (F(1,18) = 99.67, p.val < 0.00001) and that the same is true under low Fe conditions, that the additional lowering of Cu.level changes growth rates significantly (F(1,18) = 37.90, p.val < 0.00001)

```{r phia_interaction_Contrasts_Cu.level_Fe.level_Growthrate.percent, eval=TRUE}
testInteractions(lm_Growthrate.percent, fixed="Cu.level", across="Fe.level")
```

This means that there is significant growth reduction under high Cu when Fe is limiting (F(1,18) = 30.49, p.val < 0.0001). However, under low Cu, the additional Fe limitation does not have a significant additional effect on growthrate. As discussed earlier, this makes sense when looking at the actual Cu concentrations used and is not in discrepancy to former studies that did find evidence of co limitation in both strains. 

~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

<a id="FvFm"></a>

#### Fv/Fm

[Back Up](#BackUP)

First a look at the graph: 

```{r graph_FvFm, eval=TRUE}
p <- ggplot (mydata , aes(Treatment, FvFm.old))
p + geom_point(aes(group=Merged, colour=Species), size = 3)+
  labs(title="", x ="")+
  geom_point(data=mean.df , aes(Treatment, FvFm.old, size=2, colour=Species), shape = 45, size = 9)+
  guides(alpha = "none", size = "none", shape = "none")+
  expand_limits(y=0)

```

Now we start with a linear model testing for all main effects and interactions possible:

```{r lm_all_FvFm, eval=TRUE}
lm_all_FvFm <- lm(data = mydata, FvFm.old ~ (Species * Fe.level * Cu.level))
summary(lm_all_FvFm) # we need to look at the actual anova to knwo where we need to look further
anova(lm_all_FvFm) # this shows, we can take out the interaction between Species: Fe.level
```

This one shows that there is no species:Fe.level interaction. So we will take it out in our modified `lm()`:

```{r lm_FvFm, eval=TRUE}
lm_FvFm <- lm(data = mydata, FvFm.old ~ (Species + Fe.level + Cu.level)^2 - Species:Fe.level)
summary(lm_FvFm) # we need to look at the actual anova to knwo where we need to look further
plot.new()
plot(lm_FvFm)

anova(lm_FvFm) #
```

### Anova Table - FvFm

Looking at the ANOVA table for the linear model that _does not_ test for interaction between Cu.level and Species, for the data __Growthrate Percent of umax__, we see the following significant factors:


* __Species__ is  has an effect 
* __Fe. level__ has an effect 
* __Cu level__ has an effect  
* there is an __interaction__ between __Species and Cu level now: (F(1,17) = 10.1936, p.val =  0.005)
* there is an __interaction__ between __Fe level and Cu level: (F(1,18) = 6.20, p.val = 0.02)


### Using the `phia` package to look into significant effects in Fv/Fm

Again, any main effects that are included in interacting effects will be looked at through pairwise comparisons of the interacting factors

```{r phia_interaction means_FvFm, eval=TRUE}

(FvFm.means <- interactionMeans(lm_FvFm))
plot(FvFm.means)
```

This plot shows us main effects (such as species in respect to Fe.level) and first order interactions (such as Species and Cu.level). As per the "marginality principle" (see J. A. Nelder, \A reformulation of linear models," Journal of the Royal Statistical Society. Series A (General), vol. 140, no. 1, pp. 48{77, 1977.), those factors that are involved in interactions, should not be interpreted as single effects.

As we see in the upper right and lower left corner, Species and Cu  seem to have an interaction effect. Fv/Fm changes differently from high Cu to low Cu in the two species. When we look at upper middle and middle left cell, we see that Fv/Fm changes in the same way for both species in response to the same high/low Fe concentrations. This is particularly interesting as we used different Cu concentrations. This would suggest that the two strains have both started their physiological response to low iron in a similar way even though the growthrate changes do not reflect this! The interplay between Fe.level and Cu.level is seen in the middle right and lower middle cell.

#### Pairwise Comparisons

[Back Up](#BackUP)

In order to put actual numbers for the significant differences, I will proceed with pairwise comparisons by having a fixed factor and testing how it changes dependend on another factor

```{r phia_interaction_Contrasts_Species_Felevel_FvFm, eval=TRUE}
testInteractions(lm_FvFm, fixed="Species", across="Cu.level")
```

This means that the two different Cu.levels I used (high and low) does significantly change Fv/Fm in TO 1003 (F(1,17) = 32.10, p.val < 0.0001) but it does not change Fv/Fm significantly in TO 1005 (F(1,17) = 1.32, p-val > 0.2))

```{r phia_interaction_Contrasts_Fe.level_Species_FvFm, eval=TRUE}
testInteractions(lm_FvFm, fixed="Cu.level", across="Species")
```

This means that the two Species have slightly significantly different Fv/Fm under high Cu conditions (F(1,17) = 8.12, p.val = 0.01). Looking at the graph, they have almost the same Fv/Fm under control condition. However, under lowFe (which is the other high Cu condition), their Fv/Fm is sufficiently different to generate the p.val = 0.01. This could mean that TO 1003 has a more pronounced low iron response (again, even though this is not reflected at all in its growthrate decrease).

Under low Cu conditions, Fv/Fm is markedly different between the two strains (F = 61.27, p.val < 0.00001).


```{r phia_interaction_Contrasts_Fe.level_Cu.level_FvFm, eval=TRUE}
testInteractions(lm_FvFm, fixed="Fe.level", across="Cu.level")
```

This means that there is significant changes in Fv/Fm from high Cu to low Cu when integrated over both strains (F(1,17) = 25.96, p.val = 0.0002). This is likely mainly influenced by the very strong difference in TO 1003. 
WHen looking at low Fe and changing Cu from high to low, the difference in Fv/Fm is not significant anymore (F (1,17) = 3.07, pval = 0.1)

```{r phia_interaction_Contrasts_Cu.level_Fe.level_FvFm, eval=TRUE}
testInteractions(lm_FvFm, fixed="Cu.level", across="Fe.level")
```

This means that there is significant reduction in Fv/Fm across both species under high Cu when Fe is limiting (F(1,17) = 27.57, p.val = 0.0001). However, under low Cu, the additional Fe limitation does not have a significant additional effect on Fv/Fm.


<a id="Sigma"

#### Sigma

[Back Up](#BackUP)

First a look at the graph: 

```{r graph_Sigma, eval=TRUE}
p <- ggplot (mydata , aes(Treatment, Sig.old))
p + geom_point(aes(group=Merged, colour=Species), size = 3)+
  labs(title="", x ="")+
  geom_point(data=mean.df , aes(Treatment, Sig.old, size=2, colour=Species), shape = 45, size = 9)+
  guides(alpha = "none", size = "none", shape = "none")+
  expand_limits(y=0)

```

Now we start with a linear model testing for all main effects and interactions possible:

```{r lm_all_Sigma, eval=TRUE}
lm_all_Sigma <- lm(data = mydata, Sig.old ~ (Species * Fe.level * Cu.level))
summary(lm_all_Sigma) # we need to look at the actual anova to knwo where we need to look further
anova(lm_all_Sigma) # this shows, we can take out the interaction between Species: Cu.level
```

There seems to be no Fe.level : Cu.level interaction. So, let's take it out in this `lm()`:

```{r lm_Sigma, eval=TRUE}
lm_Sigma <- lm(data = mydata, Sig.old ~ (Species + Fe.level + Cu.level)^2 - Fe.level:Cu.level)
summary(lm_Sigma) # we need to look at the actual anova to knwo where we need to look further
plot.new()
plot(lm_Sigma)

anova(lm_Sigma) # this shows, we can take out the interaction between Species: Cu.level
```

### Anova Table - Sigma

Looking at the ANOVA table for the linear model that _does not_ test for interaction between Cu.level and Species, for the data __Growthrate Percent of umax__, we see the following significant factors:


* __Species__ is __not__ has an effect
* __Fe. level__ has an effect 
* __Cu level__ has an effect 
* there is  an __interaction__ between __Species and Fe level now: (F(1,14) = 13.36, p.val = 0.003)
* there is a strong __interaction__ between __Species and Cu level: (F(1,14) = 49.09, p.val < 0.00001)


### Using the `phia` package to look into significant effects regarding SIGMA

Again, any main effects that are included in interacting effects will be looked at through pairwise comparisons of the interacting factors

```{r phia_interaction means_Sigma, eval=TRUE}

(Sigma.means <- interactionMeans(lm_Sigma))
plot(Sigma.means)
```

This plot shows us main effects (such as Cu.level in regards to Fe.level) and first order interactions (such as Species and Fe.level). As per the "marginality principle" (see J. A. Nelder, \A reformulation of linear models," Journal of the Royal Statistical Society. Series A (General), vol. 140, no. 1, pp. 48{77, 1977.), those factors that are involved in interactions, should not be interpreted as single effects.

As we see in the upper right and lower left corner, Species and Cu really do seem to have very different results for Sigma.  Whenhen we look at upper middle and middle left cell, we see that Sigma also changes in a different way depending on Species and Fe level.  Differing Fe.level and Cu.level seem to change sigma in a comparable fashion.

#### Pairwise Comparisons

[Back Up](#BackUP)

In order to put actual numbers for the significant differences, I will proceed with pairwise comparisons by having a fixed factor and testing how it changes dependend on another factor

```{r phia_interaction_Contrasts_Species_Felevel_Sigma, eval=TRUE}
testInteractions(lm_Sigma, fixed="Species", across="Fe.level")
```

This means that the two different Fe.levels I used (high and low) does not significantly change Sigma in TO 1003 (F(1,14) = 2.54, p.val = 0.13) but it does change Sigma significantly in TO 1005 (F(1,14) = 41.73, p-val < 0.0001)

```{r phia_interaction_Contrasts_Fe.level_Species_Sigma, eval=TRUE}
testInteractions(lm_Sigma, fixed="Fe.level", across="Species")
```

This means that the two Species have significantly different Sigma when integrated over their respective high Fe conditions (F(1,14) = 25.26, p.val = 0.0004).
Under low iron their respective Sigmas are statistically almost the same (F (1,14) =  0, p.val = .999). Which makes sense when you look at the graph. Even though the trends are the same (i.e. under low Fe and lowFeCu, TO 1005 stays the same, whereas TO 1003 increases its Sigma). But because the unchanged Sigma of TO 1005 sits right int he middle of the low and high Sigma values of TO 1003, their integrated fixed low Fe values are the same.


```{r phia_interaction_Contrasts_Fe.level_Cu.level_Sigma, eval=TRUE}
testInteractions(lm_Sigma, fixed="Species", across="Cu.level")
```

Here, TO 1003 has a very strong Cu-effect (F(1,14) = 112.72, pval < 0.00001).
WHereas, Cu doesn;t seem to have any effect on Sigma for TO 1005 (F(1,14) = 0.02, pval = 0.88).


```{r phia_interaction_Contrasts_Cu.level_Fe.level_Sigma, eval=TRUE}
testInteractions(lm_Sigma, fixed="Cu.level", across="Species")
```

Under high Cu treatments (i.e. as response to low Fe only), the two strains show somewhat significant differences (F(1,14) = 4.89, p.val = 0.04). This is due to starting witht he same Sigma in the control treatment. THen TO 1003 shows almost no response to low Fe but TO 1005 does show a significant response to Fe. Hence, the differnece between the two strains is significant. 

This difference between the strains is even more pronounced when looking at the low Cu treatments (F (1,14) = 64.01, p.val = 0.00001). Here, TO 1003 shows almost no reponse to an added FeCu co- limitation, whereas Sigma in TO 1005 does increase significantly from low Cu to low CuFe co-limitation 


###Summary SIGMA

There are strong significant differences between TO 1003 and TO 1005 how their SIGMA changes in response to Fe, Cu, or Fe-Cu co-limitation:

__Sigma__ in __TO 1003 does not respond to lowering Fe concentrations__ (neither low Fe alone compared to high Fe, nor low FeCu compared to low Cu)

Completely diametrically different to its sister strain!!!!

__Sigma__ in __TO 1005 does not respond to lowering Cu concentrations__ (neither low Cu alone compared to high Cu, nor low FeCu compared to low Fe)
~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~


<a id="NotUsed"></a>

# Not Used

[Back Up](#BackUP)

### Tukey - HSD Method (as per * [Tutorial on posthoc-tests](http://rtutorialseries.blogspot.ca/2011/03/r-tutorial-series-anova-pairwise.html))

<a id="Tukey01"></a

[Back Up](#BackUP)

The Tukey Honest Significant Difference (HSD) method controls for the Type I error rate across multiple comparisons and is generally considered an acceptable technique. This method can be executed using the `TukeyHSD(x)` function, where `x` is a linear model object created using the `aov(formula, data)` function. Note that in this application, the aov(formula, data) function is identical to the lm(formula, data) that we are already familiar with from linear regression.

``` {r tukey_z, eval=TRUE}
TukeyHSD(aov(z)) #aov() has a different notation than anova() but gives same results as anova()
plot.new()
plot(TukeyHSD(aov(z)))

```
### What if I look at Fe levels just for TO 1003 and then just with the data for TO 1005?

<a id="lm_TO03"></a>

[Back Up](#BackUP)

For this, I will first subset my original data into TO 1003 and TO 1005, respectively. THen I will make and linear model using `lm()` followed by `anova()` on that lm object

#### Let's start with TO 1003

```{r TO03_lm_Anova, eval = TRUE}
TO03_mydata <- mydata %>% 
  filter(Species == "TO 1003")

lm_TO03 <- lm(data=mydata, Growthrate.dd.1~(Fe.level*Cu.level))
plot(lm_TO03) ##these plots are diagnostic and will give indications if the assumptions are met

anova(lm_TO03)
```

The anova table suggests that for __TO 1003__ there is a significant effect is seen for:

* Fe. level (F(1,20) = 13.68, p.val = 0.0014)
* Cu. level (F(1,20) = 58.93, p.val < 0.00001)

and that there is __NO__ interacting effect for Fe:Cu.level for TO 1003

```{r TO03_phia_interactions, eval = TRUE}
#Using `phia`
(lm_TO03.means <- interactionMeans(lm_TO03))
plot(lm_TO03.means)

```

Even though the `anova()` did not suggest an interaction... looking at the plots, it almost seems like there could be interactions

```{r TO03_phia_interaction_Contrasts_Fe.level_Cu.level, eval=TRUE}
#testInteractions(lm_TO03.means, fixed="Cu.level", across="Fe.level")
```
OK, I guess this doesn;t work. Maybe it checks if there is an interaction measured?!

But twhat does the pairwise comparison say?



~~~~~
__AND NOW ...__ we need to use `lsmeans()` to do pairwise comparisons an pinpoint which exact comparisons are the significant ones....

```{r lsmeans growthrate, eval=FALSE}
lsmeans(z_all, pairwise, ~ Fe.level | Cu.level : Species)


```


Doesn;t work, I get an error message "The model is not linear mixed effects model

```{r lm growthrate_allMain just known interaction02, eval=TRUE}
z <- lm(data=mydata, Growthrate.dd.1~(Species+Fe.level+Cu.level)^2-Species:Cu.level) #this will model the Growth rate dependend on
#three main effects (Species, Fe.level, Cu.level) and will include 
#possible interactions between Species:Fe.level, Fe.level:Cu.level 
#but NOT Species:Cu.level as we took that one out!

summary(z)

```









The following is from [Dolph Schluter's help pages](https://www.zoology.ubc.ca/~schluter/R/fit-model/)

###Fit multiple factors

When two or more categorical factors are fitted, the possibility of an interaction might also be evaluated. Remember that the order in which you enter the variables in the formula affects the ANOVA results, if the design is unbalanced. By default, R fits the variables sequentially ("type I sum of squares"), while at the same time respecting hierarchy. Each variable or interaction is tested by adding it to a model that includes only previous terms in the sequence, but not variables entered later. Hierarchy means that the main effects are fitted before the interactions, which are fitted last. No interaction term is tested without its main effects included in the model.

In the case of two factors, A and B, the linear model is as follows.
```{r Dolph01, eval=FALSE}
z <- lm(y ~ A + B, data = mydata) # no interaction term is present, or
z <- lm(y ~ A * B, data = mydata) # interaction term is included
summary(z)                        # coefficients table
confint(z, level = 0.95)          # confidence intervals for parameters
anova(z)                          # A is tested before B; interaction tested last
```

It is possible to carry out marginal fitting of terms instead ("type III sum of squares"). In this case, order of appearance of terms in the model doesn't matter, and neither does hierarchy. Each model term is tested as if it were entered last into the model. To accomplish this we need to refit the model and override R's default contrasts. Then we use the `drop1` command in place of `anova` to get the ANOVA table.

```{r Dolph02, eval=FALSE}
z <- lm(y ~ A * B, contrasts = c("contr.sum", "contr.poly"), 
    data = mydata)
drop1(z, .~., test = "F")
```

Or, we can use the `Anova` command (NOTE the capital "A" in beginning of `Anova()`) in the `car` package to give us the ANOVA table based on marginal fitting of terms ("type III sum of squares"). We again need to refit the model using different contrasts from R's default.

```{r Dolph03, eval=FALSE}
z <- lm(y ~ A * B, contrasts = c("contr.sum", "contr.poly"), 
    data = mydata)
library(car)
Anova(z, type = 3)
```

Use the visreg package to visualize model fit. Try several options to see which method is most effective. If only one factor is plotted, R plots the fit to the data for each group or level, while conditioning on the value of the other variable (adjusted to the most common category for other factor). **This makes sense only when an interaction term is not fitted**. If both factors are plotted, the fit is shown for every combination of groups (levels). In the latter case, you can choose to overlay the fits or plot in separate panels.

```{r Dolph04, eval=FALSE}
library(visreg)
visreg(z, xvar = "B", whitespace = 0.4, 
    points.par = list(cex = 1.1, col = "red"))
visreg(z, xvar = "A", by = "B", whitespace = 0.4, 
    points.par = list(cex = 1.1, col = "red"))
visreg(z, xvar = "A", by = "B", whitespace = 0.5, overlay = TRUE, 
    band = FALSE, points.par = list(cex = 1.1))
```
```{r cars}
summary(cars)
```


### Resources

* [Tutorial on linear regression](http://rtutorialseries.blogspot.ca/2009/11/r-tutorial-series-simple-linear.html)
* [Tutorial on multiple linear regression](http://rtutorialseries.blogspot.ca/2009/12/r-tutorial-series-multiple-linear.html)
* [Tutorial on posthoc-tests](http://rtutorialseries.blogspot.ca/2011/03/r-tutorial-series-anova-pairwise.html)

